---
title: "3P Turing Test: Combined Plots"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: true
    theme: flatly
    highlight: kate
    code_folding: hide
---

# Setup

Library imports

```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(tidytext)
library(janitor)
library(RColorBrewer)
library(scales)
library(xtable)
library(lmerTest)
library(brms)
library(cowplot)
library(ggpubr)
library(kableExtra)

```


Load data

```{r  message=FALSE, warning=FALSE}

game <- read.csv("data/tt_game.csv")
verdict <- read.csv("data/tt_verdict.csv")
interrogator <- read.csv("data/tt_interrogator.csv")
witness <- read.csv("data/tt_witness.csv")
message <- read.csv("data/tt_message_anonymized.csv")
profile <- read.csv("data/tt_profile.csv")
model <- read.csv("data/tt_aimodel.csv")
conversation <-  read.csv("data/tt_conversation.csv")


```


## Games

```{r  message=FALSE, warning=FALSE}

# Get profile, ai_model
games.all <- game %>%
  
  # Preprocessing
  mutate(
    created_at = as.POSIXct(created_at, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
    finished_at = as.POSIXct(finished_at, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
    day = lubridate::floor_date(created_at, "day"),
    duration = as.numeric(difftime(finished_at, created_at, units = "secs"))
  ) %>%
  
  # Verdict
  merge(
    verdict %>%
      group_by(game_id) %>%
      mutate(
        verdict_rank = row_number(desc(id))
      ) %>%
      filter(verdict_rank == 1) %>%
      rename("verdict_id" = id) %>%
      select(-interrogator_id, -verdict_rank, -created_at),
    by.x = "id", by.y = "game_id"
  ) %>%
  mutate(
    success = is_correct
  ) %>%
  
  # Interrogator
  merge(
    interrogator %>%
      mutate(
        interrogator_user_id = user_id
      ) %>%
      select(
        -lobby_wait_id, -user_id
      ),
    by.x = "interrogator_id", by.y="id"
  )  %>%
  
  # Human Witness
  merge(
    witness %>%
      filter(witness_type == "H") %>%
      mutate(
        human_witness_user_id = user_id
      ) %>%
      select(
        id, human_witness_user_id
      ),
    by.x = "human_witness_id", by.y="id"
  ) %>%
  
  # AI Witness
  merge(
    witness %>%
      filter(witness_type == "A") %>%
      select(
        id, ai_model_id
      ),
    by.x = "ai_witness_id", by.y="id"
  ) %>%
  
  # Interrogator Profile
  merge(
    profile %>%
      select(-id),
    by.x = "interrogator_user_id", by.y = "user_id"
  ) %>%
  mutate(
    age = 2025-year_of_birth,
    age = ifelse(age < 100 & age > 0, age, NA)
  ) %>%
  
  # AI Model
  merge(
    model %>%
      mutate(
        ai_model_id = id,
        ai_model = name
      ) %>%
      select(ai_model_id, ai_model, family, model_name, active),
    all.x = TRUE, all.y = FALSE
  ) %>%
  # filter(
  #   (active == "True" | is.na(active))
  # ) %>%
  
  # Messages
  # merge(
  #   message %>%
  #     group_by(
  #       game_id
  #     ) %>%
  #     summarise(
  #       n_messages = n(),
  #       total_length = sum(nchar(content)),
  #       witness_messages = sum(sender_role == "W"),
  #       total_cost = sum(cost)
  #     ),
  #   by.x = "id", by.y="game_id", all.y=F, all.x=T
  # ) %>%
  
  # At least one message from witness
  # filter (
  #   witness_messages > 0
  # ) %>%
  
  # Game index
  group_by(
    interrogator_user_id
  ) %>%
  mutate(
    interrogator_game_index = dense_rank(id)
  ) %>%
  ungroup() %>%

  # Clean model names 
  mutate(
    ai_model_long = ai_model,
    ai_model = gsub("_sona", "", ai_model),
    ai_model = gsub("_prolific", "", ai_model)
  )


# Filter games
games <- games.all


```

## Exclusions

### Prior knowledge

```{r}

profile <- profile %>%
  filter(user_id %in% games$interrogator_user_id)

profile %>%
  group_by(expt_aware) %>%
  summarize(n = n())

n.ppt.expt.aware <- nrow(profile %>%
  filter(expt_aware == TRUE))

profile <- profile %>%
  filter(expt_aware == FALSE)

games <- games %>%
  filter(interrogator_user_id %in% profile$user_id)

```

`r n.ppt.expt.aware` Participants excluded for saying they are familiar with the site.


### 2 messages

```{r}

conversation <- conversation %>%
  filter(game_id %in% games$id)

conversation <- conversation %>%
  merge(message %>%
          mutate(n_characters = nchar(content)) %>%
          group_by(conversation_id) %>%
          summarize(
            n_messages = n(),
            n_characters = sum(n_characters),
            cost = sum(cost)
            ), all.y=F, by.x="id", by.y="conversation_id")

no_interaction_games <- conversation %>%
  group_by(game_id) %>%
  summarize(min_n_messages = min(n_messages)) %>%
  filter(min_n_messages < 2) %>%
  pull(game_id)

# length(no_interaction_games)

games <- games %>% filter(!(id %in% c(no_interaction_games)))

conversation <- conversation %>%
  filter(game_id %in% games$id)

```

`r length(no_interaction_games)` Games excluded for sending fewer than 2 messages.

# Descriptive Stats

## Summary

```{r}

games %>%
  mutate(
    duration = as.numeric(duration),
    ai_model = as.factor(ai_model)
  ) %>%
  select(ai_model, duration, is_correct, confidence, interrogator_game_index) %>%
  summary()

```

## No. games

```{r}

nrow(games)

```


## No. Models
```{r}

games %>%
  group_by(ai_model) %>%
  summarize(n_games = n()) %>%
  arrange(-n_games) 

```

## No. Participants

```{r}

nrow(profile)

```

```{r}

profile %>%
  group_by(source) %>%
  summarize(n_ppts = n())


```


## Game date


```{r}

games %>%
  group_by(interrogator_user_id) %>%
  summarize(created_at = max(created_at)) %>%
  mutate(
    day = lubridate::floor_date(created_at, "day")
  ) %>%
  ggplot(aes(x = day)) +
  geom_histogram(stat="count") + 
  theme_minimal(base_size=22)

```


## Duration


```{r}

games %>%
  ggplot(aes(x = duration)) +
  geom_histogram(bins=30) + 
  theme_minimal(base_size=22) + 
  scale_x_continuous()
  

```

```{r}

games %>%
  filter(duration <= 300) %>%
  select(duration) %>%
  summary()

```

```{r}

games %>%
  filter(duration <= 300) %>%
  mutate(
    duration_bin = case_when(
      duration < 120 ~ "< 2 mins",
      duration < 300 ~ "2-5 mins",
      T ~ "5 mins"
    )
  ) %>%
  group_by(duration_bin) %>%
  summarize(n = n(), prop = n/nrow(.))

```

## No. Messages

```{r}

conversation %>%
  ggplot(aes(x = n_messages)) + 
  geom_histogram() + 
  theme_minimal()

```

```{r}

conversation %>%
  select(n_messages) %>%
  summary()

```

## No. Characters

```{r}

conversation %>%
  ggplot(aes(x = n_characters)) + 
  geom_histogram() + 
  theme_minimal()

```

```{r}

conversation %>%
  select(n_characters) %>%
  summary()

```

## Games per user

```{r}

games %>%
  group_by(interrogator_user_id) %>%
  summarize(
    n_games = n()
  ) %>%
  ggplot(aes(x = n_games)) +
  geom_bar(stat="count") + 
  theme_minimal()

```


```{r}

games %>%
  group_by(interrogator_user_id) %>%
  summarize(
    n_games = n()
  ) %>%
  group_by(n_games) %>%
  summarize(
    n = n(),
    prop = n/nrow(.)
  )

```


## Verdicts

```{r}

games %>%
  group_by(verdict) %>%
  summarize(n=n(), prop = n/nrow(games))

```

# Order effects

## Overall

```{r}

games %>%
  ggplot(aes(x = interrogator_game_index, y = as.numeric(success))) + 
  stat_summary(geom="pointrange", fun.data="mean_cl_boot") + 
  geom_smooth(method="lm", formula = "y~x") + 
  theme_minimal() + 
  labs(y = "Interrogator Accuracy", x = "Interrogator Trial Index")

```

## By Condition

```{r}

games %>%
  ggplot(aes(x = interrogator_game_index, y = as.numeric(success))) + 
  stat_summary(geom="bar", fun="mean") +
  stat_summary(geom = "errorbar", fun.data="mean_cl_boot", width = 0.2) +
  facet_wrap(facets=vars(family)) + 
  theme_minimal()  + 
  labs(y = "Interrogator Accuracy", x = "Interrogator Trial Index")

```


## First vs second persona

```{r}

games.with.persona.order <- games %>%
  filter(family %in% c("llama-persona", "gpt-4.5-persona")) %>%
  group_by(interrogator_user_id) %>%
  mutate(persona_trial_order = dense_rank(interrogator_game_index))

games.with.persona.order %>%
  ggplot(aes(x = as.factor(persona_trial_order), y = as.numeric(success))) + 
  stat_summary(geom="bar", fun="mean") + 
  stat_summary(geom="errorbar", fun.data="mean_cl_boot", width=0.2) + 
  facet_wrap(facets=vars(family)) + 
  theme_minimal() + 
  labs(y = "Interrogator Accuracy", x = "Persona Trial Order")


```

Overall

```{r}

summary(glm(success ~ persona_trial_order, family="binomial", data = games.with.persona.order))

```

LLaMa

```{r}

summary(glm(success ~ persona_trial_order, family="binomial", data = games.with.persona.order %>% filter(family == "llama-persona")))

```

GPT-4.5

```{r}

summary(glm(success ~ persona_trial_order, family="binomial", data = games.with.persona.order %>% filter(family == "gpt-4.5-persona")))
  

games.persona.first <- games.with.persona.order %>%
  filter(persona_trial_order == 1)

```

# Win Rate

## Overall


```{r}

games %>%
  group_by(success) %>%
  summarize(n(), prop = n() / nrow(games))

```


```{r}

win_rate <- games %>%
  mutate(
    success = ifelse(success==FALSE, 1, 0)
  ) %>%
  group_by(ai_model) %>%
  summarize(
    win_rate = mean(success),
    wins = sum(success),
    n_games = n(),
    losses = n_games - wins,
    .groups="drop"
  ) %>%
  filter(
    # n_games > 10
  ) %>%
  arrange(-wins)

win_rate
  

```

```{r}
win_rate <- games %>%
  mutate(
    success = ifelse(success==FALSE, 1, 0),
    source = ifelse(source == 1, "Prolific", "Undergraduates"),
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-NO-PERSONA"
    ),
  ) %>%
  # First calculate win rate by witness overall
  group_by(witness) %>%
  mutate(overall_win_rate = mean(success)) %>%
  # Then group by witness and source for detailed stats
  group_by(witness, source) %>%
  summarize(
    win_rate = mean(success),
    wins = sum(success),
    n_games = n(),
    losses = n_games - wins,
    overall_win_rate = first(overall_win_rate),
    .groups="drop"
  ) %>%
  # Sort by overall win rate first, then by source
  arrange(-overall_win_rate, source) %>%
  select(witness, source, win_rate, wins, losses, n_games)

win_rate
  

```

```{r}

# Format the win_rate data for a minimal CS conference style table
latex_table <- win_rate %>%
  # Format win_rate as percentage with one decimal place
  mutate(
    win_rate = sprintf("%.1f\\%%", win_rate * 100)
  ) %>%
  # Select columns with separate Wins, Losses, and Total
  select(
    Model = witness,
    Source = source,
    `Win Rate` = win_rate,
    Wins = wins,
    Losses = losses,
    Total = n_games
  )

# Generate the LaTeX table with minimal formatting
latex_output <- latex_table %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    align = "llcrrr",
    caption = "Win rates by model and participant source.",
    label = "tab:win_rates",
    escape = FALSE
  ) %>%
  # Simple, clean formatting without extra features
  kable_styling(
    latex_options = c("hold_position"),
    full_width = FALSE
  ) %>%
  # Group by model in a minimal way
  collapse_rows(columns = 1, latex_hline = "major", valign = "middle")

# Print the LaTeX code
cat(latex_output)


```

```{r}

win_rate <- games %>%
  mutate(
    success = ifelse(success==FALSE, 1, 0)
  ) %>%
  group_by(ai_model_long) %>%
  summarize(
    win_rate = mean(success),
    wins = sum(success),
    n_games = n(),
    losses = n_games - wins,
    .groups="drop"
  ) %>%
  filter(
    # n_games > 10
  ) %>%
  arrange(-wins)

win_rate
  

```

# Model Comparison: Overall Success Rates

```{r}
# Compare all models' success rates
model_comparison <- games %>%
  mutate(success = ifelse(success, 0, 1)) %>%
  group_by(ai_model) %>%
  summarize(
    success_rate = mean(success),
    se = sqrt(success_rate * (1 - success_rate) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  arrange(success_rate)

# Print table
model_comparison %>%
  mutate(
    success_rate = round(success_rate, 3),
    `95% CI` = paste0("[", round(success_rate - 1.96 * se, 3), ", ", 
                      round(success_rate + 1.96 * se, 3), "]"),
    vs_chance = ifelse(
      success_rate + 1.96 * se < 0.5, "**Worse than chance**",
      ifelse(success_rate - 1.96 * se > 0.5, "**Better than chance**", 
             "Not different from chance")
    )
  ) %>%
  select(ai_model, n, success_rate, `95% CI`, vs_chance) %>%
  rename(Model = ai_model, `Sample Size` = n, `Success Rate` = success_rate) %>%
  knitr::kable(caption = "Comparison of All AI Models' Success Rates")

# Visualize model comparison
ggplot(model_comparison, aes(y = reorder(ai_model, -success_rate), x = success_rate)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbarh(
    aes(xmin = success_rate - 1.96 * se, xmax = success_rate + 1.96 * se),
    height = 0.3
  ) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Success Rate",
    y = "Model",
    title = "Comparison of AI Models' Success Rates"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)
  ) +
  scale_x_continuous(limits = c(0, 1))
```

# Confidence


```{r}

c.eliza <- "#7B7B7B"
c.4o <- "#24cc24"
c.45.m <- "#B47FFA"
c.45.p <- "#9341FF"
c.l.m <- "#85BAFB"
c.l.p <- "#0064E0"

obj_is_vector <- function(x) {
  is.vector(x) && !is.factor(x)
}

p.bar <- games %>%
  mutate(
    success = ifelse(success, 0, 1),
    source = ifelse(source == 1, "Prolific", "Undergraduates"),
    source = factor(source, levels=c("Undergraduates", "Prolific")),
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-NO-PERSONA"
      ),
    b_conf = ifelse(
      verdict == "B", confidence, -1 * confidence
    ),
    s_conf = ifelse(
      success,b_conf, -1 * b_conf
    ),
  ) %>%
  ggplot(aes(y = reorder(witness, -s_conf), x = success, fill=witness)) + 
     geom_vline(xintercept=0.5, linetype="dashed", color="#888888", size=1) +
  # geom_col(aes(x = 1), fill = "#bbbbbb", alpha = 0.5) + 
  stat_summary(geom="bar", fun = "mean", alpha=0.95) +
  stat_summary(geom="errorbarh", fun.data = "mean_cl_boot",
               alpha=0.8,  height=0.2, size=1, color="#333333") +

  scale_fill_manual(
    values = c(
      "GPT-4o-NO-PERSONA"=c.4o,
      "GPT-4.5-PERSONA"=c.45.p,
      "GPT-4.5-NO-PERSONA"=c.45.m,
      "ELIZA"=c.eliza,
      "LLAMA-PERSONA"=c.l.p,
      "LLAMA-NO-PERSONA"=c.l.m
      )
  ) +
  facet_grid(rows=vars(source)) +
  theme_minimal(base_size=16) +
  theme(
      # text = element_text(family = "Microsoft Sans Serif"),
      legend.position="none",
      # axis.title = element_text(size=18),
      # axis.text = element_text(size=18),
      plot.margin = margin(0, 10, 0, 0),
      strip.background = element_blank(),
      strip.text.y = element_blank()
    ) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels=c("0%", "50%", "100%"), limits=c(0, 1)) +
  labs (
    y = "AI Witness",
    x = "Win Rate"
  )



p.jitter <- games %>%
  mutate(
    success = ifelse(success, 0, 1),
    b_conf = ifelse(
      verdict == "B", confidence, -1 * confidence
    ),
    s_conf = ifelse(
      success,b_conf, -1 * b_conf
    ),
    source = ifelse(source == 1, "Prolific", "Undergraduates"),
    source = factor(source, levels=c("Undergraduates", "Prolific")),
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-PERSONA"
      ),
  ) %>%
  ggplot(aes(x = s_conf, y = reorder(witness, -s_conf), fill=witness, color=witness)) + 
  geom_vline(xintercept = 0, linetype="dashed", linewidth=1, color="#888888") +
  geom_jitter(alpha=0.2, size=1.5, stroke=1) + 
  stat_summary(fun.data = mean_cl_boot, geom="errorbarh", size=1, height=0.15) +
  stat_summary(fun = mean, geom="point", size=4) +
  labs(
    y = "Witness Type",
    x = "Confidence"
  ) +
  scale_fill_manual(
    values = c(
      "GPT-4o-NO-PERSONA"=c.4o,
      "GPT-4.5-PERSONA"=c.45.p,
      "GPT-4.5-NO-PERSONA"=c.45.m,
      "ELIZA"=c.eliza,
      "LLAMA-PERSONA"=c.l.p,
      "LLAMA-NO-PERSONA"=c.l.m
      )
  ) +
  scale_color_manual(
    values = c(
      "GPT-4o-NO-PERSONA"=c.4o,
      "GPT-4.5-PERSONA"=c.45.p,
      "GPT-4.5-NO-PERSONA"=c.45.m,
      "ELIZA"=c.eliza,
      "LLAMA-PERSONA"=c.l.p,
      "LLAMA-NO-PERSONA"=c.l.m
      )
  ) +
  theme_minimal(base_size=16) +
  theme(
    legend.position = "none",
    # text = element_text(family = "Microsoft Sans Serif"),
      # plot.title = element_text(size = 22, hjust = 0.25),
      # axis.title = element_text(size=22),
      # axis.text = element_text(size=18),
      plot.margin = margin(0, 10, 0, 10)
    ) + 
  facet_grid(rows=vars(source))


p.winrate.bar.jitter <- ggarrange(p.bar,
          p.jitter + 
               theme(axis.title.y = element_blank(),
                     axis.text.y = element_blank()),
          nrow=1)

# p.winrate.bar.jitter

ggsave("img/win_rate_composite_bar_jitter.png", p.winrate.bar.jitter, width=7, height=5)

ggsave("img/win_rate_composite_bar_jitter.svg", p.winrate.bar.jitter, width=14, height=10)

```


# Reasons

```{r}

reason_classes <- read.csv("data/reason_classifications_4o.csv") %>%
  merge(games %>% select(id, ai_model, success, source, reason), by.x = "game_id", by.y = "id"
  ) %>%
  merge(
    read.csv("data/3p_reason_scheme.csv"), by="class"
  )


all_unique_categories <- c("Linguistic Style", "Situational Awareness", "Content & Knowledge", "Personality & Emotions", "Interaction Dynamics", "Direct", "Meta", "Other")

pal.Categories <- 
setNames(brewer.pal(length(all_unique_categories), "Set2"), all_unique_categories)


```

```{r}

reason_classes %>%
  group_by(game_id, category) %>%
  summarize(category = first(category)) %>%
  group_by(category) %>%
  summarize(n = n(), prop = n / nrow(.)) %>%
  arrange(-n)

```

```{r}

reason_classes %>%
  group_by(class, short_name) %>%
  summarize(n = n()) %>%
  arrange(-n)

```
## Plots

### All Reasons


```{r}

reason_classes %>%
  group_by(short_name, category) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    .groups="drop"
    ) %>%
  arrange(-prop) %>%
  filter(n > 3) %>%
  ggplot(aes(y = reorder(short_name, prop), x = prop, fill = category)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  theme_minimal(base_size=18) +
  theme(legend.position = "none") +
  facet_wrap(~category, scales="free_y") +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  ) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories)

ggsave("img/all_reasons.png", width=14, height=7)

```

### Top Reasons

```{r}


p.reasons.top <- reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category
  ) %>%
  group_by(reason_class, reason_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(games),
    .groups="drop"
  ) %>%
  arrange(-prop) %>%
  head(16) %>%
  ggplot(aes(y = reorder(reason_class, prop), x = prop, fill = reason_category)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  theme_minimal(base_size=20) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  )  +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = c(0.7, 0.15),
    legend.background = element_rect(fill="#FFFFFF88", linewidth = 0,
                                     color="transparent"),
    legend.text = element_text(size=14, lineheight = 28),
    legend.margin=margin(c(-10,1,1,1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                             label.hjust = 1))


```


### By Accuracy

```{r}

reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category
  ) %>%
  merge(games %>% select(id), by.x = "game_id", by.y = "id") %>%
  mutate(accuracy = ifelse(success, 1, 0)) %>%
  group_by(reason_class, reason_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    acc = mean(accuracy),
    .groups="drop"
  ) %>%
  filter(n>10) %>%
  arrange(-acc) %>%
  rbind(head(., 4)) %>%
  tail(8) %>%
  select(reason_class, n, acc) %>%
  arrange(-acc)

```

```{r}

p.reasons.acc <- reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category
  ) %>%
  merge(games %>% select(id), by.x = "game_id", by.y = "id") %>%
  mutate(accuracy = ifelse(success, 1, 0)) %>%
  group_by(reason_class, reason_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    acc = mean(accuracy),
    se = sd(accuracy) / sqrt(n()),  # Calculate standard error
    lower_ci = acc - 1.96 * se,  # 95% CI lower bound
    upper_ci = acc + 1.96 * se,  # 95% CI upper bound
    .groups="drop"
  ) %>%
  filter(n>15) %>%
  arrange(-acc) %>%
  rbind(head(., 8)) %>%
  tail(16) %>%
  ggplot(aes(y = reorder(reason_class, acc), x = acc, fill = reason_category)) + 
  geom_bar(stat="identity") +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0.2) +
  # geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  theme_minimal(base_size=20) +
  labs(
    x = "Mean Accuracy",
    y = "Reason Class"
  )  +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = c(0.75, 0.15),
    legend.background = element_rect(fill="#FFFFFF88", linewidth = 0,
                                     color="transparent"),
    legend.text = element_text(size=14, lineheight = 28),
    legend.margin=margin(c(-10,1,1,1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                             label.hjust = 1))

ggsave("img/reasons_acc.pdf", width=7, height=7)

ggsave("img/reasons_acc.png", width=7, height=7, bg="white")

```


### Combined Reason Plot

```{r}


library(egg)

p.strat <- ggarrange(
    p.reasons.top,
    p.reasons.acc + theme(
      axis.title.y = element_blank(),
      legend.position="none"),
    nrow=1)

ggsave("img/reasons_combined.png", p.strat, width=14, height=7, bg="white")

```

## By Success

```{r}


reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category,
    success = ifelse(success, "Selected Human", "Selected AI")
  ) %>%
  group_by(reason_class, reason_category, success) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    .groups="drop"
  ) %>%
  arrange(-prop) %>%
  head(16) %>%
  ggplot(aes(y = reorder(reason_class, prop), x = prop, fill = reason_category)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  facet_grid(cols=vars(success)) + 
  theme_minimal(base_size=20) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  )  +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = c(0.85, 0.15),
    legend.background = element_rect(fill="#FFFFFF88", linewidth = 0,
                                     color="transparent"),
    legend.text = element_text(size=14, lineheight = 28),
    legend.margin=margin(c(-10,1,1,1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                             label.hjust = 1))


```

```{r}


# Calculate top reasons for each model separately
reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category,
    success = ifelse(success, "Correct Verdicts", "Incorrect Verdicts")
  ) %>%
  # Count occurrences by reason class and model
  group_by(success, reason_class, reason_category) %>%
  summarize(
    n = n(),
    .groups = "drop"
  ) %>%
  # Calculate proportion within each model
  group_by(success) %>%
  mutate(
    total_reasons = sum(n),
    prop = n / total_reasons
  ) %>%
  # Get top N reasons for each model independently
  group_by(success) %>%
  arrange(success, desc(prop)) %>%
  slice_head(n = 15) %>%  # Adjust number as needed
  # Create the plot with independent y-axes
  ggplot(aes(y = reorder_within(reason_class, prop, success), 
             x = prop, 
             fill = reason_category)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust = 1.25, size = 3, color = "#333333") +
  # This is the key part - free_y allows different y-axes
  facet_wrap(facets = vars(success), scales = "free_y") +
  # Required when using reorder_within
  scale_y_reordered() +
  theme_minimal(base_size = 24) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  ) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    strip.text = element_text(size=22),
    legend.position = c(0.87, 0.15),
    legend.background = element_rect(fill = "#FFFFFF88", linewidth = 0,
                                    color = "transparent"),
    legend.text = element_text(size = 16, lineheight = 32),
    legend.margin = margin(c(-10, 1, 1, 1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                           label.hjust = 1))


ggsave("img/top_reasons_by_success.png", width=14, height=7)

```

## By Source

```{r}

reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category,
    source = ifelse(source == 1, "Prolific", "Undergraduates")
  ) %>%
  group_by(reason_class, reason_category, source) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    .groups="drop"
  ) %>%
  arrange(-prop) %>%
  head(16) %>%
  ggplot(aes(y = reorder(reason_class, prop), x = prop, fill = reason_category)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  facet_grid(cols=vars(source)) + 
  theme_minimal(base_size=20) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  )  +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = c(0.85, 0.15),
    legend.background = element_rect(fill="#FFFFFF88", linewidth = 0,
                                     color="transparent"),
    legend.text = element_text(size=14, lineheight = 28),
    legend.margin=margin(c(-10,1,1,1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                             label.hjust = 1))


```

## By Model

```{r}

library(tidytext)

# Calculate top reasons for each model separately
reason_classes %>%
  mutate(
    reason_class = short_name,
    reason_category = category,
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-NO-PERSONA"
      ),
  ) %>%
  # Count occurrences by reason class and model
  group_by(witness, reason_class, reason_category) %>%
  summarize(
    n = n(),
    .groups = "drop"
  ) %>%
  # Calculate proportion within each model
  group_by(witness) %>%
  mutate(
    total_reasons = sum(n),
    prop = n / total_reasons
  ) %>%
  # Get top N reasons for each model independently
  group_by(witness) %>%
  arrange(witness, desc(prop)) %>%
  slice_head(n = 10) %>%  # Adjust number as needed
  # Create the plot with independent y-axes
  ggplot(aes(y = reorder_within(reason_class, prop, witness), 
             x = prop, 
             fill = reason_category)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust = 1.25, size = 3, color = "#333333") +
  # This is the key part - free_y allows different y-axes
  facet_wrap(facets = vars(witness), scales = "free_y") +
  # Required when using reorder_within
  scale_y_reordered() +
  theme_minimal(base_size = 20) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  ) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = "none",
    legend.background = element_rect(fill = "#FFFFFF88", linewidth = 0,
                                    color = "transparent"),
    legend.text = element_text(size = 14, lineheight = 28),
    legend.margin = margin(c(-10, 1, 1, 1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  )

ggsave("img/top_reasons_by_model.png", width=16, height=8)

```

### Only model passes

```{r}

# Calculate top reasons for each model separately
reason_classes %>%
  filter(success == FALSE) %>%
  mutate(
    reason_class = short_name,
    reason_category = category,
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-NO-PERSONA"
      ),
  ) %>%
  # Count occurrences by reason class and model
  group_by(witness, reason_class, reason_category) %>%
  summarize(
    n = n(),
    .groups = "drop"
  ) %>%
  # Calculate proportion within each model
  group_by(witness) %>%
  mutate(
    total_reasons = sum(n),
    prop = n / total_reasons
  ) %>%
  # Get top N reasons for each model independently
  group_by(witness) %>%
  arrange(witness, desc(prop)) %>%
  slice_head(n = 10) %>%  # Adjust number as needed
  # Create the plot with independent y-axes
  ggplot(aes(y = reorder_within(reason_class, prop, witness), 
             x = prop, 
             fill = reason_category)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust = 1.25, size = 3, color = "#333333") +
  # This is the key part - free_y allows different y-axes
  facet_wrap(facets = vars(witness), scales = "free_y") +
  # Required when using reorder_within
  scale_y_reordered() +
  theme_minimal(base_size = 20) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  ) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = "none",
    legend.background = element_rect(fill = "#FFFFFF88", linewidth = 0,
                                    color = "transparent"),
    legend.text = element_text(size = 14, lineheight = 28),
    legend.margin = margin(c(-10, 1, 1, 1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  )

ggsave("img/top_reasons_by_model_pass.png", width=16, height=8)

```

### Only model fails

```{r}

# Calculate top reasons for each model separately
reason_classes %>%
  filter(success == TRUE) %>%
  mutate(
    reason_class = short_name,
    reason_category = category,
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-NO-PERSONA"
      ),
  ) %>%
  # Count occurrences by reason class and model
  group_by(witness, reason_class, reason_category) %>%
  summarize(
    n = n(),
    .groups = "drop"
  ) %>%
  # Calculate proportion within each model
  group_by(witness) %>%
  mutate(
    total_reasons = sum(n),
    prop = n / total_reasons
  ) %>%
  # Get top N reasons for each model independently
  group_by(witness) %>%
  arrange(witness, desc(prop)) %>%
  slice_head(n = 10) %>%  # Adjust number as needed
  # Create the plot with independent y-axes
  ggplot(aes(y = reorder_within(reason_class, prop, witness), 
             x = prop, 
             fill = reason_category)) + 
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust = 1.25, size = 3, color = "#333333") +
  # This is the key part - free_y allows different y-axes
  facet_wrap(facets = vars(witness), scales = "free_y") +
  # Required when using reorder_within
  scale_y_reordered() +
  theme_minimal(base_size = 20) +
  labs(
    x = "Proportion of Reasons",
    y = "Reason Class"
  ) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = "none",
    legend.background = element_rect(fill = "#FFFFFF88", linewidth = 0,
                                    color = "transparent"),
    legend.text = element_text(size = 14, lineheight = 28),
    legend.margin = margin(c(-10, 1, 1, 1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  )

ggsave("img/top_reasons_by_model_fails.png", width=16, height=8)

```



# Strategy tagging

```{r}

# Load strategy data
strategies <- read.csv("data/strategy_classifications_4o.csv") %>%
  mutate(
    code = class,
  )

# Load strategy scheme
strategy_scheme <- read.csv("data/tt_strategyclass.csv") %>%
  filter(
    code != "6f"
  ) %>%
  mutate(
    strategy_class = name,
    strategy_category = category
  )

# Merge strategy data with scheme
strategy_classes <- strategies %>%
  merge(strategy_scheme, by="code")


all_unique_categories <- c("Linguistic Style", "Situational Awareness", "Knowledge & Reasoning", "Social & Emotional", "Small Talk", "Direct", "Meta", "Other")

pal.Categories <- 
setNames(brewer.pal(length(all_unique_categories), "Set2"), all_unique_categories)


```

## Top

```{r}

strategy_classes %>%
  group_by(game_id, strategy_category) %>%
  summarize(strategy_category = first(strategy_category)) %>%
  group_by(strategy_category) %>%
  summarize(n = n(), prop = n / nrow(games)) %>%
  arrange(-n)

```

```{r}

p.strategy.top <- strategy_classes %>%
  group_by(strategy_class, strategy_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(games),
    .groups="drop"
  ) %>%
  arrange(-prop) %>%
  head(16) %>%
  ggplot(aes(y = reorder(strategy_class, prop), x = prop, fill = strategy_category)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  theme_minimal(base_size=20) +
  labs(
    x = "Proportion of Games",
    y = "Strategy Class"
  )  +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.1)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = c(0.7, 0.15),
    legend.background = element_rect(fill="#FFFFFF88", linewidth = 0,
                                     color="transparent"),
    legend.text = element_text(size=14, lineheight = 28),
    legend.margin=margin(c(-10,1,1,1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                             label.hjust = 1))


ggsave("img/strategies_top.pdf", width=7, height=7)

ggsave("img/strategies_top.png", width=7, height=7, bg="white")

```

## By subcategory

```{r}

strategy_classes %>%
  group_by(strategy_class, strategy_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    .groups="drop"
    ) %>%
  arrange(-prop) %>%
  ggplot(aes(y = reorder(strategy_class, prop), x = prop, fill = strategy_category)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  theme_minimal(base_size=18) +
  theme(legend.position = "none") +
  facet_wrap(~strategy_category, scales="free_y") +
  labs(
    x = "Proportion of Strategies",
    y = "Strategy Class"
  ) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.05)) +
  scale_fill_manual(values=pal.Categories)


ggsave("img/strategies_by_cat.png", width=14, height=7)

```


### By Accuracy

```{r}

strategy_classes %>%
  merge(games %>% select(id, success), by.x = "game_id", by.y = "id") %>%
  mutate(accuracy = ifelse(success, 1, 0)) %>%
  group_by(strategy_class, strategy_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    acc = mean(accuracy),
    .groups="drop"
  ) %>%
  filter(n>10) %>%
  arrange(-acc) %>%
  rbind(head(., 4)) %>%
  tail(8) %>%
  select(strategy_class, n, acc) %>%
  arrange(-acc)

```

```{r}

p.strat.acc <- strategy_classes %>%
  merge(games %>% select(id, success), by.x = "game_id", by.y = "id") %>%
  mutate(accuracy = ifelse(success, 1, 0)) %>%
  group_by(strategy_class, strategy_category) %>%
  summarize(
    n = n(),
    prop = n / nrow(.),
    acc = mean(accuracy),
    se = sd(accuracy) / sqrt(n()),  # Calculate standard error
    lower_ci = acc - 1.96 * se,  # 95% CI lower bound
    upper_ci = acc + 1.96 * se,  # 95% CI upper bound
    .groups="drop"
  ) %>%
  filter(n>10) %>%
  arrange(-acc) %>%
  rbind(head(., 8)) %>%
  tail(16) %>%
  ggplot(aes(y = reorder(strategy_class, acc), x = acc, fill = strategy_category)) + 
  geom_bar(stat="identity") +
  geom_errorbarh(aes(xmin = lower_ci, xmax = upper_ci), height = 0.2) +
  # geom_text(aes(label = n), vjust = 0.5, hjust=1.25, size=3, color="#333333") +
  theme_minimal(base_size=20) +
  labs(
    x = "Mean Accuracy",
    y = "Strategy Class"
  )  +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25)) +
  scale_fill_manual(values = pal.Categories) + 
  theme(
    legend.position = c(0.75, 0.15),
    legend.background = element_rect(fill="#FFFFFF88", linewidth = 0,
                                     color="transparent"),
    legend.text = element_text(size=14, lineheight = 28),
    legend.margin=margin(c(-10,1,1,1)),
    legend.title = element_blank(),
    legend.spacing.y = unit(0.2, 'cm')
  ) +
  guides(fill = guide_legend(label.position = "left",
                             label.hjust = 1))

ggsave("img/strategies_acc.pdf", width=7, height=7)

ggsave("img/strategies_acc.png", width=7, height=7, bg="white")

```

## Combined Strategy Plot

```{r}


library(egg)

p.strat <- ggarrange(
    p.strategy.top,
    p.strat.acc + theme(
      axis.title.y = element_blank(),
      legend.position="none"),
    nrow=1)

ggsave("img/strategies_combined.png", p.strat, width=14, height=7, bg="white")

```


  
# Demographics

## Summary


```{r}

library(cowplot)


user_stats <- profile %>%
  merge(
    games %>%
      group_by(interrogator_user_id) %>%
      summarize(
        n_games = n(),
        accuracy = mean(success),
        ),
    by.x = "user_id", by.y = "interrogator_user_id",
    all.y = FALSE
  ) %>%
  mutate(
    age = 2025 - year_of_birth,
    source = ifelse(source == 1, "Prolific", "Undergraduates"),
  )

c.prolific <- "#76AEC3"
c.undergrads <- "#0044B4"

```

```{r}

summary(user_stats %>%
          mutate(gender = as.factor(gender)))

mean(user_stats %>% filter(age > 0, age < 100) %>% pull(age))
sd(user_stats %>% filter(age > 0, age < 100) %>% pull(age))

```

## Distribution

```{r}

p.age.dist <- user_stats %>%
  filter(
    age > 0,
    age < 100
  ) %>%
  mutate(Study = source) %>%
  ggplot(aes(x = age, fill=Study)) + 
  geom_histogram(bins=10, color="white", stroke=0, position="dodge") +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(
    legend.position = "none"
  ) +
  labs(
    x = "Age",
    y = "Frequency"
  )

p.age.dist

```

```{r}


p.edu.dist <- user_stats %>%
  filter(education > 0) %>%
  ggplot(aes(x = factor(education), fill=source)) + 
  geom_bar(stat="count", position="dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "Formal Education",
    y = "Frequency"
  ) +
  scale_x_discrete(
    labels=c("HS", "UG", "PG")
  )

p.edu.dist

```


```{r}


p.freq.dist <- user_stats %>%
  filter(chatbot_interaction_frequency > 0) %>%
  ggplot(aes(x = factor(chatbot_interaction_frequency), fill=source)) +
  geom_bar(stat="count", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "Chatbot Interaction",
    y = "Frequency"
  ) +
  scale_x_discrete(
    labels=c("Never", "Month", "Week", "Day")
  )

p.freq.dist

```

```{r}


p.knowledge.dist <- user_stats %>%
  filter(familiarity_with_GPT > 0) %>%
  ggplot(aes(x = factor(familiarity_with_GPT), fill=source)) + 
  geom_bar(stat="count", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "LLM Knowledge",
    y = "Frequency"
  ) +
    scale_x_discrete(
    labels=c("None", "Some", "High", "Research")
  )

p.knowledge.dist

```

No Games

```{r}


p.games.dist <- user_stats %>%
  ggplot(aes(x = n_games, fill=source)) + 
  geom_bar(stat="count", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "No. Interrogator Games",
    y = "Frequency"
  )

p.games.dist

```


Gender

```{r}

p.gender.dist <- user_stats %>%
  filter(gender %in% c("M", "F", "N")) %>%
  ggplot(aes(x = factor(gender), fill=source)) + 
  geom_bar(stat="count", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "Gender",
    y = "Frequency"
  ) +
  scale_x_discrete(
    labels=c("F", "M", "N.B.")
  )

p.gender.dist


```


Intelligence

```{r}

p.intelligence.dist <- user_stats %>%
  filter(intelligence > 0) %>%
  ggplot(aes(x = factor(intelligence), fill=source)) + 
  geom_bar(stat="count", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "AI Intelligence",
    y = "Frequency"
  )

p.intelligence.dist


```

AI Emotion

```{r}

p.emotion.dist <- user_stats %>%
  filter(emotion > 0) %>%
  ggplot(aes(x = factor(emotion), fill=source)) +
  geom_bar(stat="count", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "AI Emotion",
    y = "Frequency"
  )

p.emotion.dist


```

AI Emotion

```{r}

p.accest.dist <- user_stats %>%
  mutate(
    accuracy_estimate = pmin(accuracy_estimate, n_games),
    acc_est = accuracy_estimate / n_games
  ) %>%
  ggplot(aes(x = acc_est, fill=source)) +
  geom_histogram(bins=5, color="white", position = "dodge")  +
  scale_fill_manual(
    values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)
  ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "Accuracy Estimate",
    y = "Frequency"
  ) + 
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25))

p.accest.dist


```




```{r}

study_legend = ggpubr::get_legend(p.age.dist + theme(legend.position="bottom"))

p.demo.dist <- ggpubr::ggarrange(p.gender.dist,
          p.edu.dist + 
               theme(axis.title.y = element_blank()),
          p.age.dist + 
               theme(axis.title.y = element_blank()),
          p.knowledge.dist,
          p.freq.dist + 
               theme(axis.title.y = element_blank()),
          p.games.dist +
               theme(axis.title.y = element_blank()),
          p.intelligence.dist,
          p.emotion.dist +
               theme(axis.title.y = element_blank()),
          p.accest.dist +
               theme(axis.title.y = element_blank()),
          nrow=3, ncol=3,
          widths = c(5, 4, 4),
          common.legend=T,
          legend = "bottom",
          legend.grob = study_legend
          )

p.demo.dist


ggsave("img/demo_dist.png",p.demo.dist, width=14, height=10)


```

## Accuracy

```{r}


p.age <- user_stats %>%
  filter(
    age > 0,
    age < 100
  ) %>%
  ggplot(aes(x = age, y = accuracy, fill=source, color=source)) + 
  geom_smooth(formula="y~x", method="lm") +
  scale_color_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  stat_summary_bin(fun.data="mean_cl_boot", geom="pointrange", bins=20, alpha=0.8) +
  theme_minimal(
    base_size=24
  ) + 
  theme(
    legend.position = "none"
  ) +
  labs(
    x = "Age",
    y = "Accuracy"
  ) + 
  scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25))

p.age

```

```{r}


p.edu <- user_stats %>%
  filter(education > 0) %>%
  ggplot(aes(x = factor(education), y = accuracy, fill=source)) + 
  stat_summary(geom="bar", fun="mean", position="dodge")  +
  stat_summary(geom="errorbar", width=0.5, fun.data = mean_cl_boot, color="#444444", position=position_dodge(width=0.95)) + 
  theme_minimal(
    base_size=24
  ) + 
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  theme(legend.position = "none") +
  labs(
    x = "Formal Education",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25)) + 
  # coord_cartesian(ylim=c(0,1)) + 
  scale_x_discrete(
    labels=c("HS", "UG", "PG")
  )

p.edu

```


```{r}


p.freq <- user_stats %>%
  filter(chatbot_interaction_frequency > 0) %>%
  ggplot(aes(x = factor(chatbot_interaction_frequency), y = accuracy, fill=source)) + 
  stat_summary(geom="bar", fun="mean", position="dodge")  +
  stat_summary(geom="errorbar", width=0.5, fun.data = mean_cl_boot, position=position_dodge(width=0.95))  + 
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "Chatbot Interaction",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25), limits=c(0,1)) + 
  scale_x_discrete(
    labels=c("Never", "Monthly", "Weekly", "Daily")
  )

p.freq

```

```{r}


p.knowledge <- user_stats %>%
  filter(familiarity_with_GPT > 0) %>%
  ggplot(aes(x = factor(familiarity_with_GPT), y = accuracy, fill=source)) + 
  stat_summary(geom="bar", fun="mean", position="dodge")  +
  stat_summary(geom="errorbar", width=0.5, fun.data = mean_cl_boot,
               position=position_dodge(width=0.95))  +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  labs(
    x = "LLM Knowledge",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25), limits=c(0,1)) + 
    scale_x_discrete(
    labels=c("None", "Some", "High", "Research")
  )

p.knowledge

```

No Games

```{r}


p.games <- games %>%
  mutate(
    accuracy = ifelse(success, 1, 0),
    source = ifelse(source == 1, "Prolific", "Undergraduates")
    ) %>%
  ggplot(aes(x = interrogator_game_index, y = accuracy, color=source, fill=source)) + 
  geom_smooth(method="lm", formula="y~x") +
  stat_summary(fun.data="mean_cl_boot", geom="pointrange", alpha=0.8) +
  theme_minimal(
    base_size=24
  ) + 
  theme(
    legend.position = "none"
  ) +
  scale_color_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  labs(
    x = "No. Games",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25), limits=c(0,1)) + 
  scale_x_continuous(breaks = seq(0, 10, by=1))

p.games
```


Gender

```{r}

p.gender <- user_stats %>%
  mutate(Study = source) %>%
  filter(gender %in% c("M", "F", "N")) %>%
  ggplot(aes(x = factor(gender), y = accuracy, fill=Study)) +
  stat_summary(geom="bar", fun="mean", position="dodge")  +
  stat_summary(geom="errorbar", width=0.5, fun.data = mean_cl_boot, color="#444444", position=position_dodge(width=0.95)) + 
  theme_minimal(
    base_size=24
  ) + 
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  theme(legend.position = "none") +
  labs(
    x = "Gender",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25), limits=c(0,1)) + 
  scale_x_discrete(
    labels=c("F", "M", "N.B.")
  )

p.gender


```

AI Intelligence

```{r}

p.intelligence <- user_stats %>%
  filter(intelligence > 0) %>%
  ggplot(aes(x = factor(intelligence), y = accuracy, fill=source)) + 
  stat_summary(geom="bar", fun="mean", position="dodge")  +
  stat_summary(geom="errorbar", width=0.5, fun.data = mean_cl_boot, color="#444444", position=position_dodge(width=0.95)) + 
  theme_minimal(
    base_size=24
  ) + 
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  theme(legend.position = "none") +
  labs(
    x = "AI Intelligence",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25), limits=c(0,1))

p.intelligence
```

AI Emotion

```{r}

p.emotion <- user_stats %>%
  filter(emotion > 0) %>%
  ggplot(aes(x = factor(emotion), y = accuracy, fill=source)) +
  stat_summary(geom="bar", fun="mean", position="dodge")  +
  stat_summary(geom="errorbar", width=0.5, fun.data = mean_cl_boot, color="#444444", position=position_dodge(width=0.95)) + 
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads) ) +
  theme_minimal(
    base_size=24
  ) + 
  theme(legend.position = "none") +
  labs(
    x = "AI Emotion",
    y = "Accuracy"
  ) +
  scale_y_continuous(
    labels = scales::percent, breaks = seq(0, 1, by = 0.25), limits=c(0,1))

p.emotion

```

Accuracy Estimate

```{r}

p.accest <- user_stats %>%
  mutate(
    accuracy_estimate = pmin(accuracy_estimate, n_games),
    acc_est = accuracy_estimate / n_games
  ) %>%
  ggplot(aes(x = acc_est, y = accuracy, fill=source, color=source)) +
  stat_summary_bin(fun.data="mean_cl_boot", geom="pointrange", bins=5, alpha=0.8) +
  geom_smooth(method="lm", formula="y~x") +
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  scale_color_manual(values=c("Prolific"=c.prolific, "Undergraduates"=c.undergrads)) +
  theme_minimal(
    base_size=24
  ) + 
  theme(
    legend.position = "none"
  ) +
  labs(
    x = "Accuracy Estimate",
    y = "Accuracy"
  ) + 
  scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25)) + 
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25))

p.accest

```

```{r}

obj_is_vector <- function(x) is.vector(x) && !is.factor(x)

study_legend <- ggpubr::get_legend(p.gender + theme(legend.position = "bottom"))

p.demo <- ggpubr::ggarrange(p.gender,
          p.edu + 
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(),
                     axis.title.y = element_blank()),
          p.age + 
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(),
                     axis.title.y = element_blank()),
          p.knowledge,
          p.freq + 
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(),
                     axis.title.y = element_blank()),
          p.games +
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(),
                     axis.title.y = element_blank()),
          p.intelligence,
          
          p.emotion + 
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(),
                     axis.title.y = element_blank()),
          
          p.accest +
               theme(axis.text.y = element_blank(),
                     axis.ticks.y = element_blank(),
                     axis.title.y = element_blank()),
          nrow=3, ncol=3,
          widths = c(5, 4, 4),
          common.legend=T,
          legend = "bottom",
          legend.grob = study_legend
          )

ggsave("img/demo_effects.pdf", p.demo, width=14, height=10)

ggsave("img/demo_effects.png", p.demo, width=14, height=10)

```

# Confidence


## Calibration

```{r}

p.conf.calibration <- games %>%
  mutate(
    confidence_to_human = ifelse(success, abs(confidence), -abs(confidence)) / 100,
    abs_confidence = abs(confidence) / 100,
    study = ifelse(source == 1, "Prolific", "Undergraduate"),
    witness = recode(
      ai_model,
      eliza="ELIZA",
      `gpt-4o_minimal`="GPT-4o-NO-PERSONA",
      `gpt-4.5_minimal`="GPT-4.5-NO-PERSONA",
      `gpt-4.5_quinn`="GPT-4.5-PERSONA",
      `llama-405b_quinn`="LLAMA-PERSONA",
      `llama-405b_minimal`="LLAMA-NO-PERSONA"
      ),
  ) %>%
  ggplot(aes(x = abs_confidence, y = as.numeric(success), color=study, fill=study)) + 
  stat_summary_bin(fun.data="mean_cl_boot", geom="pointrange", bins=5, alpha=0.8) +
  geom_smooth(method="lm", formula="y~x") +
  theme_minimal(
    base_size=24
  ) +
  labs(
    x = "Confidence",
    y = "Accuracy",
    color = "Study",
    fill = "Study"
  ) + 
  scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25)) +
  scale_x_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.25)) +
  scale_color_manual(values=c("Prolific"=c.prolific, "Undergraduate"=c.undergrads)) +
  scale_fill_manual(values=c("Prolific"=c.prolific, "Undergraduate"=c.undergrads)) +
  facet_wrap(~witness) + 
  theme(
    legend.position = "bottom"
  )

# ggsave("img/win_rate_composite_bar_jitter.svg", , width=14, height=10)

p.conf.calibration

ggsave("img/confidence_calibration.pdf", p.conf.calibration, width=14, height=10)

ggsave("img/confidence_calibration.png", p.conf.calibration, width=14, height=10)

```
