---
title: "3P Turing Test: Pre-registered Analyses (Prolific)"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: true
    theme: flatly
    highlight: kate
    code_folding: hide
---

# Setup

Library imports

```{r message=FALSE, warning=FALSE}

# source("download_data_3p.R")

library(tidyverse)
library(janitor)
library(RColorBrewer)
library(scales)
library(xtable)
library(lmerTest)
library(brms)

```


Load data

```{r  message=FALSE, warning=FALSE}

game <- read.csv("data/tt_game.csv")
verdict <- read.csv("data/tt_verdict.csv")
interrogator <- read.csv("data/tt_interrogator.csv")
witness <- read.csv("data/tt_witness.csv")
message <- read.csv("data/tt_message_anonymized.csv")
profile <- read.csv("data/tt_profile.csv")
model <- read.csv("data/tt_aimodel.csv")
conversation <-  read.csv("data/tt_conversation.csv")

```


## Games

```{r  message=FALSE, warning=FALSE}



# Get profile, ai_model

games.all <- game %>%
  
  # Preprocessing
  mutate(
    created_at = as.POSIXct(created_at, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
    finished_at = as.POSIXct(finished_at, format = "%Y-%m-%dT%H:%M:%SZ", tz = "UTC"),
    day = lubridate::floor_date(created_at, "day"),
    duration = as.numeric(difftime(finished_at, created_at, units = "secs"))
  ) %>%
  
  # Verdict
  merge(
    verdict %>%
      group_by(game_id) %>%
      mutate(
        verdict_rank = row_number(desc(id))
      ) %>%
      filter(verdict_rank == 1) %>%
      rename("verdict_id" = id) %>%
      select(-interrogator_id, -verdict_rank, -created_at),
    by.x = "id", by.y = "game_id"
  ) %>%
  mutate(
    success = is_correct
  ) %>%
  
  # Interrogator
  merge(
    interrogator %>%
      mutate(
        interrogator_user_id = user_id
      ) %>%
      select(
        -lobby_wait_id, -user_id
      ),
    by.x = "interrogator_id", by.y="id"
  )  %>%
  
  # Human Witness
  merge(
    witness %>%
      filter(witness_type == "H") %>%
      mutate(
        human_witness_user_id = user_id
      ) %>%
      select(
        id, human_witness_user_id
      ),
    by.x = "human_witness_id", by.y="id"
  ) %>%
  
  # AI Witness
  merge(
    witness %>%
      filter(witness_type == "A") %>%
      select(
        id, ai_model_id
      ),
    by.x = "ai_witness_id", by.y="id"
  ) %>%
  
  # Interrogator Profile
  merge(
    profile %>%
      filter(
        source == 1,
        study == 3,
        ) %>%
      select(-id),
    by.x = "interrogator_user_id", by.y = "user_id"
  ) %>%
  mutate(
    age = 2025-year_of_birth,
    age = ifelse(age < 100 & age > 0, age, NA)
  ) %>%
  
  # AI Model
  merge(
    model %>%
      mutate(
        ai_model_id = id,
        ai_model = name
      ) %>%
      select(ai_model_id, ai_model, family, model_name, active),
    all.x = TRUE, all.y = FALSE
  ) %>%
  
  # Game index
  group_by(
    interrogator_user_id
  ) %>%
  mutate(
    interrogator_game_index = dense_rank(id)
  ) %>%
  ungroup()


# Filter games
games <- games.all

```

## Exclusions

### Prior knowledge

```{r}

profile <- profile %>%
  filter(user_id %in% games$interrogator_user_id)

n.pre <- nrow(profile)

profile %>%
  group_by(expt_aware) %>%
  summarize(n = n())

profile %>%
  filter(expt_aware == TRUE) %>%
  select(expt_aware, expt_aware_details)

n.ppt.expt.aware <- nrow(profile %>%
  filter(expt_aware == TRUE))

profile <- profile %>%
  filter(expt_aware == FALSE)

games <- games %>%
  filter(interrogator_user_id %in% profile$user_id)

```

`r n.ppt.expt.aware` Participants excluded for saying they are familiar with the site.


### 2 messages

```{r}

conversation <- conversation %>%
  filter(game_id %in% games$id)

conversation <- conversation %>%
  merge(message %>%
          mutate(n_characters = nchar(content)) %>%
          group_by(conversation_id) %>%
          summarize(
            n_messages = n(),
            n_characters = sum(n_characters),
            cost = sum(cost)
            ), all.y=F, by.x="id", by.y="conversation_id")

no_interaction_games <- conversation %>%
  group_by(game_id) %>%
  summarize(min_n_messages = min(n_messages)) %>%
  filter(min_n_messages < 2) %>%
  pull(game_id)

# length(no_interaction_games)

games <- games %>% filter(!(id %in% c(no_interaction_games)))

conversation <- conversation %>%
  filter(game_id %in% games$id)

```

`r length(no_interaction_games)` Games excluded for sending fewer than 2 messages.

### Exclusions Summary

```{r}

# Summary of how many ppts there were before exclusions, how many were excluded in each cat and how many are retained

summary_table <- data.frame(
  Category = c("Total participants", "Excluded for prior knowledge", "Excluded for < 2 messages", "Remaining participants"),
  Count = c(n.pre, n.ppt.expt.aware, length(no_interaction_games), nrow(profile))
)

summary_table

```

# Descriptive Stats

## Summary

```{r}

games %>%
  mutate(
    duration = as.numeric(duration),
    ai_model = as.factor(ai_model)
  ) %>%
  select(ai_model, duration, is_correct, confidence, interrogator_game_index) %>%
  summary()

```

## No. games

```{r}

nrow(games)

```


## No. Models
```{r}

games %>%
  group_by(ai_model) %>%
  summarize(n_games = n()) %>%
  arrange(-n_games) 

```

## No. Participants

```{r}

length(unique(games$interrogator_user_id))

```


## Game date


```{r}

games %>%
  group_by(interrogator_user_id) %>%
  summarize(created_at = max(created_at)) %>%
  mutate(
    day = lubridate::floor_date(created_at, "day")
  ) %>%
  ggplot(aes(x = day)) +
  geom_histogram(stat="count") + 
  theme_minimal(base_size=22)

```


## Duration


```{r}

games %>%
  ggplot(aes(x = duration)) +
  geom_histogram(bins=30) + 
  theme_minimal(base_size=22) + 
  scale_x_continuous()
  

```

```{r}

games %>%
  filter(duration <= 300) %>%
  select(duration) %>%
  summary()

```

## No. Messages

```{r}

conversation %>%
  ggplot(aes(x = n_messages)) + 
  geom_histogram() + 
  theme_minimal()

```

```{r}

conversation %>%
  select(n_messages) %>%
  summary()

```

## No. Characters

```{r}

conversation %>%
  ggplot(aes(x = n_characters)) + 
  geom_histogram() + 
  theme_minimal()

```

```{r}

conversation %>%
  select(n_characters) %>%
  summary()

```

## Games per user

```{r}

games %>%
  group_by(interrogator_user_id) %>%
  summarize(
    n_games = n()
  ) %>%
  ggplot(aes(x = n_games)) +
  geom_bar(stat="count") + 
  theme_minimal()

```


## Verdicts

```{r}

games %>%
  group_by(verdict) %>%
  summarize(n=n(), prop = n/nrow(games))

```

# Order effects

## Overall

```{r}

games %>%
  ggplot(aes(x = interrogator_game_index, y = as.numeric(success))) + 
  stat_summary(geom="pointrange", fun.data="mean_cl_boot") + 
  geom_smooth(method="lm", formula = "y~x") + 
  theme_minimal() + 
  labs(y = "Interrogator Accuracy", x = "Interrogator Trial Index")

```

## By Condition

```{r}

games %>%
  ggplot(aes(x = interrogator_game_index, y = as.numeric(success))) + 
  stat_summary(geom="bar", fun="mean") +
  stat_summary(geom = "errorbar", fun.data="mean_cl_boot", width = 0.2) +
  facet_wrap(facets=vars(family)) + 
  theme_minimal()  + 
  labs(y = "Interrogator Accuracy", x = "Interrogator Trial Index")

```


## First vs second persona

```{r}

games.with.persona.order <- games %>%
  filter(family %in% c("llama-persona", "gpt-4.5-persona")) %>%
  group_by(interrogator_user_id) %>%
  mutate(persona_trial_order = dense_rank(interrogator_game_index))

games.with.persona.order %>%
  ggplot(aes(x = as.factor(persona_trial_order), y = as.numeric(success))) + 
  stat_summary(geom="bar", fun="mean") + 
  stat_summary(geom="errorbar", fun.data="mean_cl_boot", width=0.2) + 
  facet_wrap(facets=vars(family)) + 
  theme_minimal() + 
  labs(y = "Interrogator Accuracy", x = "Persona Trial Order")


```

Overall

```{r}

summary(glm(success ~ persona_trial_order, family="binomial", data = games.with.persona.order))

```

LLaMa

```{r}

summary(glm(success ~ persona_trial_order, family="binomial", data = games.with.persona.order %>% filter(family == "llama-persona")))

```

GPT-4.5

```{r}

summary(glm(success ~ persona_trial_order, family="binomial", data = games.with.persona.order %>% filter(family == "gpt-4.5-persona")))
  

games.persona.first <- games.with.persona.order %>%
  filter(persona_trial_order == 1)

```

# Model Comparison: Overall Success Rates

```{r}
# Compare all models' success rates
model_comparison <- games %>%
  mutate(success = ifelse(success, 0, 1)) %>%
  group_by(ai_model) %>%
  summarize(
    success_rate = mean(success),
    se = sqrt(success_rate * (1 - success_rate) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  arrange(success_rate)

# Print table
model_comparison %>%
  mutate(
    success_rate = round(success_rate, 3),
    `95% CI` = paste0("[", round(success_rate - 1.96 * se, 3), ", ", 
                      round(success_rate + 1.96 * se, 3), "]"),
    vs_chance = ifelse(
      success_rate + 1.96 * se < 0.5, "**Worse than chance**",
      ifelse(success_rate - 1.96 * se > 0.5, "**Better than chance**", 
             "Not different from chance")
    )
  ) %>%
  select(ai_model, n, success_rate, `95% CI`, vs_chance) %>%
  rename(Model = ai_model, `Sample Size` = n, `Success Rate` = success_rate) %>%
  knitr::kable(caption = "Comparison of All AI Models' Success Rates")

# Visualize model comparison
ggplot(model_comparison, aes(y = reorder(ai_model, -success_rate), x = success_rate)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbarh(
    aes(xmin = success_rate - 1.96 * se, xmax = success_rate + 1.96 * se),
    height = 0.3
  ) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Success Rate",
    y = "Model",
    title = "Comparison of AI Models' Success Rates"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)
  ) +
  scale_x_continuous(limits = c(0, 1))
```


# H1: LLMs indistinguishable from humans in Turing test context

```{r}
# Format p-values for display
format_pvalue <- function(p) {
  if (p < 0.001) return("< 0.001")
  if (p < 0.01) return(format(round(p, 3), nsmall = 3))
  return(format(round(p, 2), nsmall = 2))
}

# Modified function to run one-sided binomial tests
run_binomial_test <- function(data_filtered, hypothesis_name, condition_desc, alternative = "two.sided") {
  model <- glm(success ~ 1, family = "binomial", data = data_filtered)
  model_summary <- summary(model)
  
  # Extract key statistics
  coef_est <- model_summary$coefficients[1, 1]
  std_error <- model_summary$coefficients[1, 2]
  z_value <- coef_est / std_error
  success_prob <- plogis(coef_est)
  ci <- confint(model)
  success_ci <- plogis(ci)
  
  # Calculate p-value based on specified alternative
  if (alternative == "less") {
    # For testing if success_prob < 0.5 (log odds < 0)
    p_value <- pnorm(z_value) # Lower tail
  } else if (alternative == "greater") {
    # For testing if success_prob > 0.5 (log odds > 0)
    p_value <- 1 - pnorm(z_value) # Upper tail
  } else {
    # Two-sided test (default from summary)
    p_value <- model_summary$coefficients[1, 4]
  }
  
  # Print results in a structured format
  cat("------------------------------------------------------\n")
  cat(paste0(hypothesis_name, ": ", condition_desc, "\n"))
  cat("------------------------------------------------------\n")
  cat("Alternative hypothesis:", alternative, "\n")
  print(model_summary)
  cat("\n")
  cat("Estimated success probability:", round(success_prob, 3), "\n")
  cat("95% CI for success probability:", round(success_ci[1], 3), "to", round(success_ci[2], 3), "\n")
  
  # Format p-value for display
  if (p_value < 0.001) {
    p_value_display <- "p < 0.001"
  } else if (p_value < 0.01) {
    p_value_display <- paste0("p = ", format(round(p_value, 3), nsmall = 3))
  } else {
    p_value_display <- paste0("p = ", format(round(p_value, 2), nsmall = 2))
  }
  
  # Conclusion based on the alternative hypothesis
  if (alternative == "less") {
    if (p_value < 0.05) {
      conclusion <- paste0("**Participants are significantly worse than chance at identifying this model. (", p_value_display, ")**")
    } else {
      conclusion <- paste0("Participants are not significantly worse than chance at identifying this model. (", p_value_display, ")")
    }
  } else if (alternative == "greater") {
    if (p_value < 0.05) {
      conclusion <- paste0("**Participants are significantly better than chance at identifying this model. (", p_value_display, ")**")
    } else {
      conclusion <- paste0("Participants are not significantly better than chance at identifying this model. (", p_value_display, ")")
    }
  } else {
    if (p_value < 0.05) {
      if (success_prob > 0.5) {
        conclusion <- paste0("**Participants are significantly better than chance at identifying this model. (", p_value_display, ")**")
      } else {
        conclusion <- paste0("**Participants are significantly worse than chance at identifying this model. (", p_value_display, ")**")
      }
    } else {
      conclusion <- paste0("Participants are not significantly different from chance at identifying this model. (", p_value_display, ")")
    }
  }
  
  cat(conclusion, "\n\n")
  
  return(list(
    model = model, 
    success_prob = success_prob, 
    p_value = p_value, 
    significant = p_value < 0.05,
    conclusion = conclusion
  ))
}

# Alternative approach using exact binomial test
run_exact_binomial_test <- function(data_filtered, hypothesis_name, condition_desc, alternative = "less") {
  # Count successes and total trials
  n_success <- sum(data_filtered$success)
  n_trials <- nrow(data_filtered)
  
  # Run binomial test (one-sided)
  binom_result <- binom.test(n_success, n_trials, p = 0.5, alternative = alternative)
  
  # Extract results
  success_prob <- binom_result$estimate
  p_value <- binom_result$p.value
  ci <- binom_result$conf.int
  
  # Print results
  cat("------------------------------------------------------\n")
  cat(paste0(hypothesis_name, ": ", condition_desc, "\n"))
  cat("------------------------------------------------------\n")
  cat("Alternative hypothesis:", alternative, "\n")
  cat("Number of successes:", n_success, "out of", n_trials, "\n")
  cat("Estimated success probability:", round(success_prob, 3), "\n")
  cat("95% CI for success probability:", round(ci[1], 3), "to", round(ci[2], 3), "\n")
  
  # Format p-value
  if (p_value < 0.001) {
    p_value_display <- "p < 0.001"
  } else if (p_value < 0.01) {
    p_value_display <- paste0("p = ", format(round(p_value, 3), nsmall = 3))
  } else {
    p_value_display <- paste0("p = ", format(round(p_value, 2), nsmall = 2))
  }
  
  # Conclusion
  if (alternative == "less") {
    if (p_value < 0.05) {
      conclusion <- paste0("**Participants are significantly worse than chance at identifying this model. (", p_value_display, ")**")
    } else {
      conclusion <- paste0("Participants are not significantly worse than chance at identifying this model. (", p_value_display, ")")
    }
  } else if (alternative == "greater") {
    if (p_value < 0.05) {
      conclusion <- paste0("**Participants are significantly better than chance at identifying this model. (", p_value_display, ")**")
    } else {
      conclusion <- paste0("Participants are not significantly better than chance at identifying this model. (", p_value_display, ")")
    }
  }
  
  cat(conclusion, "\n\n")
  
  return(list(
    binom_result = binom_result,
    success_prob = success_prob,
    p_value = p_value,
    significant = p_value < 0.05,
    conclusion = conclusion
  ))
}
```

## H1a: ELIZA (manipulation check)

```{r}
h1a_results <- run_binomial_test(
  games %>% filter(ai_model == "eliza_prolific"),
  "H1a", 
  "Human accuracy at determining ELIZA is an AI (should be > 0.5)",
  "greater"
)
```

## H1b: Llama with persona prompt

```{r}
# First persona trials only
h1b_first_results <- run_binomial_test(
  games.persona.first %>% filter(ai_model == "llama-405b_quinn_prolific"),
  "H1b (first persona trial only)", 
  "Human accuracy at detecting Llama with persona (test if not > 0.5)",
  "greater"
)

# All trials
h1b_all_results <- run_binomial_test(
  games %>% filter(ai_model == "llama-405b_quinn_prolific"),
  "H1b (all trials)", 
  "Human accuracy at detecting Llama with persona (test if not > 0.5)",
  "greater"
)
```

## H1c: GPT-4.5 with persona prompt

```{r}
# First persona trials only
h1c_first_results <- run_binomial_test(
  games.persona.first %>% filter(ai_model == "gpt-4.5_quinn_prolific"),
  "H1c (first persona trial only)", 
  "Human accuracy at detecting GPT-4.5 with persona (test if not > 0.5)",
  "greater"
)

# All trials
h1c_all_results <- run_binomial_test(
  games %>% filter(ai_model == "gpt-4.5_quinn_prolific"),
  "H1c (all trials)", 
  "Human accuracy at detecting GPT-4.5 with persona (test if not > 0.5)",
  "greater"
)
```


## Summary of H1 Results

```{r}

h1.corrected.pvals <- c(h1a_results$p_value, 
             h1b_first_results$p_value, h1b_all_results$p_value,
             h1c_first_results$p_value, h1c_all_results$p_value) / 2

# Summarize H1 results
h1_summary <- data.frame(
  Hypothesis = c("H1a: ELIZA", 
                 "H1b: Llama (first)", "H1b: Llama (all)",
                 "H1c: GPT-4.5 (first)", "H1c: GPT-4.5 (all)"),
  Accuracy = c(h1a_results$success_prob, 
                  h1b_first_results$success_prob, h1b_all_results$success_prob,
                  h1c_first_results$success_prob, h1c_all_results$success_prob),
  p_value = c(h1a_results$p_value, 
             h1b_first_results$p_value, h1b_all_results$p_value,
             h1c_first_results$p_value, h1c_all_results$p_value),
  Significant = c(h1a_results$significant,
                 h1b_first_results$significant, h1b_all_results$significant,
                 h1c_first_results$significant, h1c_all_results$significant),
  p_value_corrected = h1.corrected.pvals
)

# Print summary table
h1_summary %>%
  mutate(
    Accuracy = round(Accuracy, 3),
    p_value_display = sapply(p_value, format_pvalue),
    p_value_corrected = sapply(p_value_corrected, format_pvalue),
    Significance = ifelse(Significant, "**Significant**", "Not Significant")
  ) %>%
  select(Hypothesis, Accuracy, p_value_display, p_value_corrected, Significance) %>%
  rename(`P-value` = p_value_display, `P-value (corrected)` = p_value_display) %>%
  knitr::kable(caption = "Summary of H1 Tests")
```

# H2: Prompting strategies affect participant accuracy

## H2a: Persona vs no-persona prompts

```{r}
# Create a dataset for H2 analysis
h2_data <- games %>% 
  filter(ai_model %in% c(
    "llama-405b_minimal_prolific", "llama-405b_quinn_prolific", 
    "gpt-4.5_minimal_prolific", "gpt-4.5_quinn_prolific"
  )) %>%
  mutate(
    prompt_type = ifelse(grepl("minimal", ai_model), "no-persona", "persona"),
    model_name = ifelse(grepl("llama", ai_model), "Llama", "GPT-4.5")
  )

# Run mixed effects model
h2a_model <- lme4::glmer(
  success ~ prompt_type + (1 | interrogator_user_id) + (1 | model_name),
  family = "binomial",
  data = h2_data
)

# Print results
cat("H2a: Effect of prompt type (persona vs no-persona) on participant accuracy\n")
cat("------------------------------------------------------\n")
print(summary(h2a_model))

# Extract key statistics
h2a_coef <- fixef(h2a_model)["prompt_typepersona"]
h2a_se <- sqrt(diag(vcov(h2a_model)))["prompt_typepersona"]
h2a_p <- 2 * (1 - pnorm(abs(h2a_coef/h2a_se)))

# Format p-value
if (h2a_p < 0.001) {
  h2a_p_display <- "p < 0.001"
} else if (h2a_p < 0.01) {
  h2a_p_display <- paste0("p = ", format(round(h2a_p, 3), nsmall = 3))
} else {
  h2a_p_display <- paste0("p = ", format(round(h2a_p, 2), nsmall = 2))
}

# Interpret results
if (h2a_p < 0.05) {
  if (h2a_coef > 0) {
    cat(paste0("**Persona prompting significantly increases participant accuracy compared to no-persona prompting. (", h2a_p_display, ")**\n"))
  } else {
    cat(paste0("**Persona prompting significantly decreases participant accuracy compared to no-persona prompting. (", h2a_p_display, ")**\n"))
  }
} else {
  cat(paste0("There is no significant difference in participant accuracy between persona and no-persona prompting. (", h2a_p_display, ")\n"))
}

# Visualize results
h2_data %>%
  group_by(prompt_type, model_name) %>%
  summarize(
    success_rate = mean(success),
    se = sqrt(success_rate * (1 - success_rate) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = prompt_type, y = success_rate, fill = model_name)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(
    aes(ymin = success_rate - 1.96 * se, ymax = success_rate + 1.96 * se),
    position = position_dodge(width = 0.9),
    width = 0.2
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Prompt Type",
    y = "Accuracy",
    fill = "Model",
    title = "Effect of Prompt Type on participant accuracy"
  ) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 1))
```

# H3: Advanced LLMs indistinguishable without specific persona

## H3a: GPT-4.5 with minimal prompt

```{r}
h3a_results <- run_binomial_test(
  games %>% filter(ai_model == "gpt-4.5_minimal_prolific"),
  "H3a", 
  "Human accuracy at detecting GPT-4.5 with minimal prompt (test if not > 0.5)"
)
```

## H3b: Llama with minimal prompt

```{r}
h3b_results <- run_binomial_test(
  games %>% filter(ai_model == "llama-405b_minimal_prolific"),
  "H3b", 
  "Human accuracy at detecting Llama with minimal prompt (test if not > 0.5)"
)
```



## Summary of H3 Results

```{r}


h3.corrected.pvals <- c(h3a_results$p_value, h3b_results$p_value) / 2


# Summarize H3 results
h3_summary <- data.frame(
  Hypothesis = c("H3a: GPT-4.5 (no-persona)", "H3b: Llama (no-persona)"),
  Accuracy = c(h3a_results$success_prob, h3b_results$success_prob),
  p_value = c(h3a_results$p_value, h3b_results$p_value),
  Significant = c(h3a_results$significant, h3b_results$significant),
  p_value_corrected = h3.corrected.pvals
)

# Print summary table
h3_summary %>%
  mutate(
    Accuracy = round(Accuracy, 3),
    p_value_display = sapply(p_value, format_pvalue),
    p_value_corrected = sapply(p_value_corrected, format_pvalue),
    Significance = ifelse(Significant, "**Significant**", "Not Significant")
  ) %>%
  select(Hypothesis, Accuracy, p_value_display, p_value_corrected, Significance) %>%
  rename(`P-value` = p_value_display, `P-value (corrected)` = p_value_corrected) %>%
  knitr::kable(caption = "Summary of H3 Tests")

```

# H4: Modern LLMs outperform older conversational AI

## H4a: GPT-4.5 vs ELIZA

```{r}
# With no-persona prompt
h4a1_model <- glm(
  success ~ ai_model, 
  family = "binomial",
  data = games %>% 
    filter(ai_model %in% c("gpt-4.5_minimal_prolific", "eliza_prolific"))
)

# Print results
cat("H4a: GPT-4.5 (no-persona) vs ELIZA\n")
cat("------------------------------------------------------\n")
print(summary(h4a1_model))

# With persona prompt
h4a2_model <- glm(
  success ~ ai_model, 
  family = "binomial",
  data = games %>% 
    filter(ai_model %in% c("gpt-4.5_quinn_prolific", "eliza_prolific"))
)

# Print results
cat("\nH4a: GPT-4.5 (persona) vs ELIZA\n")
cat("------------------------------------------------------\n")
print(summary(h4a2_model))

# Extract key statistics and interpret
models <- list(
  list(
    name = "GPT-4.5 (no-persona) vs ELIZA", 
    model = h4a1_model,
    coef_name = names(coef(h4a1_model))[2]
  ),
  list(
    name = "GPT-4.5 (persona) vs ELIZA",
    model = h4a2_model,
    coef_name = names(coef(h4a2_model))[2]
  )
)

for (m in models) {
  coef_val <- coef(m$model)[m$coef_name]
  p_val <- summary(m$model)$coefficients[m$coef_name, "Pr(>|z|)"]
  
  # Format p-value
  if (p_val < 0.001) {
    p_display <- "p < 0.001"
  } else if (p_val < 0.01) {
    p_display <- paste0("p = ", format(round(p_val, 3), nsmall = 3))
  } else {
    p_display <- paste0("p = ", format(round(p_val, 2), nsmall = 2))
  }
  
  cat("\nFor", m$name, ":\n")
  if (p_val < 0.05) {
    if (coef_val > 0) {
      cat(paste0("**", gsub(" vs ELIZA", "", m$name), " significantly outperforms ELIZA. (", p_display, ")**\n"))
    } else {
      cat(paste0("**", gsub(" vs ELIZA", "", m$name), " performs significantly worse than ELIZA. (", p_display, ")**\n"))
    }
  } else {
    cat(paste0("There is no significant difference between ", gsub(" vs ELIZA", "", m$name), " and ELIZA. (", p_display, ")\n"))
  }
}
```

## H4b: Llama vs ELIZA

```{r}
# With no-persona prompt
h4b1_model <- glm(
  success ~ ai_model, 
  family = "binomial",
  data = games %>% 
    filter(ai_model %in% c("llama-405b_minimal_prolific", "eliza_prolific"))
)

# Print results
cat("H4b: Llama (no-persona) vs ELIZA\n")
cat("------------------------------------------------------\n")
print(summary(h4b1_model))

# With persona prompt
h4b2_model <- glm(
  success ~ ai_model, 
  family = "binomial",
  data = games %>% 
    filter(ai_model %in% c("llama-405b_quinn_prolific", "eliza_prolific"))
)

# Print results
cat("\nH4b: Llama (persona) vs ELIZA\n")
cat("------------------------------------------------------\n")
print(summary(h4b2_model))

# Extract key statistics and interpret
models <- list(
  list(
    name = "Llama (no-persona) vs ELIZA", 
    model = h4b1_model,
    coef_name = names(coef(h4b1_model))[2]
  ),
  list(
    name = "Llama (persona) vs ELIZA",
    model = h4b2_model,
    coef_name = names(coef(h4b2_model))[2]
  )
)

for (m in models) {
  coef_val <- coef(m$model)[m$coef_name]
  p_val <- summary(m$model)$coefficients[m$coef_name, "Pr(>|z|)"]
  
  # Format p-value
  if (p_val < 0.001) {
    p_display <- "p < 0.001"
  } else if (p_val < 0.01) {
    p_display <- paste0("p = ", format(round(p_val, 3), nsmall = 3))
  } else {
    p_display <- paste0("p = ", format(round(p_val, 2), nsmall = 2))
  }
  
  cat("\nFor", m$name, ":\n")
  if (p_val < 0.05) {
    if (coef_val > 0) {
      cat(paste0("**", gsub(" vs ELIZA", "", m$name), " significantly outperforms ELIZA. (", p_display, ")**\n"))
    } else {
      cat(paste0("**", gsub(" vs ELIZA", "", m$name), " performs significantly worse than ELIZA. (", p_display, ")**\n"))
    }
  } else {
    cat(paste0("There is no significant difference between ", gsub(" vs ELIZA", "", m$name), " and ELIZA. (", p_display, ")\n"))
  }
}
```

## H4c: GPT-4o vs ELIZA

```{r}
# Check if GPT-4o data exists in the dataset

h4c_model <- glm(
  success ~ ai_model, 
  family = "binomial",
  data = games %>% 
    filter(ai_model %in% c("gpt-4o_minimal_prolific", "eliza_prolific"))
)

# Print results
cat("H4c: GPT-4o vs ELIZA\n")
cat("------------------------------------------------------\n")
print(summary(h4c_model))

# Extract key statistics and interpret
coef_val <- coef(h4c_model)[2]  # Assuming the second coefficient is for GPT-4o
p_val <- summary(h4c_model)$coefficients[2, "Pr(>|z|)"]

# Format p-value
if (p_val < 0.001) {
  p_display <- "p < 0.001"
} else if (p_val < 0.01) {
  p_display <- paste0("p = ", format(round(p_val, 3), nsmall = 3))
} else {
  p_display <- paste0("p = ", format(round(p_val, 2), nsmall = 2))
}
  
cat("\nFor GPT-4o vs ELIZA:\n")
if (p_val < 0.05) {
  if (coef_val > 0) {
    cat(paste0("**GPT-4o significantly outperforms ELIZA. (", p_display, ")**\n"))
  } else {
    cat(paste0("**GPT-4o performs significantly worse than ELIZA. (", p_display, ")**\n"))
  }
} else {
  cat(paste0("There is no significant difference between GPT-4o and ELIZA. (", p_display, ")\n"))
}
```

## Summary of H4 Results

```{r}
# Create a summary table of all H4 results if all models were tested
if (exists("h4a1_model") && exists("h4a2_model") && exists("h4b1_model") && exists("h4b2_model")) {
  h4_models <- list(
    list(name = "GPT-4.5 (no-persona) vs ELIZA", model = h4a1_model, coef_index = 2),
    list(name = "GPT-4.5 (persona) vs ELIZA", model = h4a2_model, coef_index = 2),
    list(name = "Llama (no-persona) vs ELIZA", model = h4b1_model, coef_index = 2),
    list(name = "Llama (persona) vs ELIZA", model = h4b2_model, coef_index = 2)
  )
  
  # Add GPT-4o if available
  if (exists("h4c_model")) {
    h4_models <- c(h4_models, list(list(name = "GPT-4o vs ELIZA", model = h4c_model, coef_index = 2)))
  }
  
  # Extract results
  h4_summary <- data.frame(
    Comparison = sapply(h4_models, function(m) m$name),
    Coefficient = sapply(h4_models, function(m) coef(m$model)[m$coef_index]),
    p_value = sapply(h4_models, function(m) summary(m$model)$coefficients[m$coef_index, "Pr(>|z|)"])
  )
  
  # Format and print
  h4_summary %>%
    mutate(
      Odds_Ratio = exp(Coefficient),
      Coefficient = round(Coefficient, 3),
      Odds_Ratio = round(Odds_Ratio, 3),
      p_value_display = sapply(p_value, format_pvalue),
      Significant = ifelse(p_value < 0.05, "**Significant**", "Not Significant")
    ) %>%
    select(Comparison, Coefficient, Odds_Ratio, p_value_display, Significant) %>%
    rename(`P-value` = p_value_display) %>%
    knitr::kable(caption = "Summary of H4 Tests (Modern LLMs vs ELIZA)")
}
```

# H5: LLMs with persona judged human more often than humans

## H5a: GPT-4.5 with persona prompt

```{r}
h5a_results <- run_binomial_test(
  games %>% filter(ai_model == "gpt-4.5_quinn_prolific"),
  "H5a", 
  "Testing if GPT-4.5 with persona is judged human more often than humans (success < 0.5)"
)
```

## H5b: Llama with persona prompt

```{r}
h5b_results <- run_binomial_test(
  games %>% filter(ai_model == "llama-405b_quinn_prolific"),
  "H5b", 
  "Testing if Llama with persona is judged human more often than humans (success < 0.5)"
)
```



## Summary of H5 Results

```{r}

h5.pvals.corrected = p.adjust(c(h5a_results$p_value, h5b_results$p_value), method="fdr")

# Summarize H5 results
h5_summary <- data.frame(
  Hypothesis = c("H5a: GPT-4.5 (persona)", "H5b: Llama (persona)"),
  Accuracy = c(h5a_results$success_prob, h5b_results$success_prob),
  p_value = c(h5a_results$p_value, h5b_results$p_value),
  p_value_corrected = h5.pvals.corrected,
  Significant = c(h5a_results$significant, h5b_results$significant)
)

# Print summary table
h5_summary %>%
  mutate(
    Accuracy = round(Accuracy, 3),
    p_value_display = sapply(p_value, format_pvalue),
    p_value_corrected = sapply(p_value_corrected, format_pvalue),
    Significance = ifelse(Significant & Accuracy < 0.5, 
                         "**AI judged more human than humans**", 
                         "Not significant")
  ) %>%
  select(Hypothesis, Accuracy, p_value_display, p_value_corrected, Significance) %>%
  rename(`P-value` = p_value_display, `P-value (corrected)` = p_value_corrected) %>%
  knitr::kable(caption = "Summary of H5 Tests")
```

# H6: LLMs without persona judged human more often than humans

## H6a: GPT-4.5 with minimal prompt

```{r}
h6a_results <- run_binomial_test(
  games %>% filter(ai_model == "gpt-4.5_minimal_prolific"),
  "H6a", 
  "Testing if GPT-4.5 with minimal prompt is judged human more often than humans (success < 0.5)"
)
```

## H6b: Llama with minimal prompt

```{r}
h6b_results <- run_binomial_test(
  games %>% filter(ai_model == "llama-405b_minimal_prolific"),
  "H6b", 
  "Testing if Llama with minimal prompt is judged human more often than humans (success < 0.5)"
)
```

## Summary of H6 Results

```{r}


h6.pvals.corrected = p.adjust(c(h6a_results$p_value, h6b_results$p_value), method="fdr")

# Summarize H6 results
h6_summary <- data.frame(
  Hypothesis = c("H6a: GPT-4.5 (no-persona)", "H6b: Llama (no-persona)"),
  Accuracy = c(h6a_results$success_prob, h6b_results$success_prob),
  p_value = c(h6a_results$p_value, h6b_results$p_value),
  p_value_corrected = h6.pvals.corrected,
  Significant = c(h6a_results$significant, h6b_results$significant)
)

# Print summary table
h6_summary %>%
  mutate(
    Accuracy = round(Accuracy, 3),
    p_value_display = sapply(p_value, format_pvalue),
    p_value_corrected = sapply(p_value_corrected, format_pvalue),
    Significance = ifelse(Significant & Accuracy < 0.5, 
                         "**AI judged more human than humans**", 
                         "Not significant")
  ) %>%
  select(Hypothesis, Accuracy, p_value_display, p_value_corrected, Significance) %>%
  rename(`P-value` = p_value_display, `P-value (corrected)` = p_value_corrected) %>%
  knitr::kable(caption = "Summary of H6 Tests")
```

# Additional Analyses

## Non-inferiority Testing for H1 and H3

As specified in our pre-registration, we conduct non-inferiority testing to test whether model pass rates are significantly above a threshold of 0.35.

```{r}
# Function for non-inferiority testing
run_noninf_test <- function(data_filtered, hypothesis_name, condition_desc, threshold = 0.35) {
  model <- glm(success ~ 1, family = "binomial", data = data_filtered %>% mutate(success = ifelse(success, 0, 1)))
  coef_est <- coef(model)[1]
  se <- sqrt(diag(vcov(model)))[1]
  
  # Convert from logit to probability scale
  prob_est <- plogis(coef_est)
  
  # Calculate one-sided confidence interval
  logit_threshold <- log(threshold / (1 - threshold))
  z_score <- 1.645  # One-sided 95% CI
  margin <- z_score * se
  
  # Test if lower bound of CI exceeds threshold
  lower_bound_logit <- coef_est - margin
  lower_bound_prob <- plogis(lower_bound_logit)
  
  noninferior <- lower_bound_logit > logit_threshold
  
  # Print results
  cat("------------------------------------------------------\n")
  cat(paste0(hypothesis_name, " (Non-inferiority test): ", condition_desc, "\n"))
  cat("------------------------------------------------------\n")
  cat("Estimated success probability:", round(prob_est, 3), "\n")
  cat("Non-inferiority threshold:", threshold, "\n")
  cat("Lower bound of one-sided 95% CI:", round(lower_bound_prob, 3), "\n")
  
  if (noninferior) {
    cat(paste0("**Result: The model's performance is significantly above the threshold of ", threshold, "**\n\n"))
  } else {
    cat(paste0("Result: Cannot conclude that the model's performance is significantly above the threshold of ", threshold, "\n\n"))
  }
  
  return(list(
    prob_est = prob_est,
    lower_bound = lower_bound_prob,
    noninferior = noninferior
  ))
}

# Apply non-inferiority tests for H1 and H3
# H1b: Llama with persona
h1b_noninf <- run_noninf_test(
  games.persona.first %>% filter(ai_model == "llama-405b_quinn_prolific"),
  "H1b", 
  "Testing if Llama with persona is non-inferior to threshold"
)

# H1c: GPT-4.5 with persona
h1c_noninf <- run_noninf_test(
  games.persona.first %>% filter(ai_model == "gpt-4.5_quinn_prolific"),
  "H1c", 
  "Testing if GPT-4.5 with persona is non-inferior to threshold"
)

# H3a: GPT-4.5 with minimal prompt
h3a_noninf <- run_noninf_test(
  games %>% filter(ai_model == "gpt-4.5_minimal_prolific"),
  "H3a", 
  "Testing if GPT-4.5 with minimal prompt is non-inferior to threshold"
)

# H3b: Llama with minimal prompt
h3b_noninf <- run_noninf_test(
  games %>% filter(ai_model == "llama-405b_minimal_prolific"),
  "H3b", 
  "Testing if Llama with minimal prompt is non-inferior to threshold"
)

# Summarize non-inferiority tests
noninf_summary <- data.frame(
  Hypothesis = c("H1b: Llama (persona)", "H1c: GPT-4.5 (persona)",
                "H3a: GPT-4.5 (no-persona)", "H3b: Llama (no-persona)"),
  Success_Rate = c(h1b_noninf$prob_est, h1c_noninf$prob_est,
                  h3a_noninf$prob_est, h3b_noninf$prob_est),
  Lower_Bound = c(h1b_noninf$lower_bound, h1c_noninf$lower_bound,
                 h3a_noninf$lower_bound, h3b_noninf$lower_bound),
  Non_Inferior = c(h1b_noninf$noninferior, h1c_noninf$noninferior,
                  h3a_noninf$noninferior, h3b_noninf$noninferior)
)

# Print summary table
noninf_summary %>%
  mutate(
    Success_Rate = round(Success_Rate, 3),
    Lower_Bound = round(Lower_Bound, 3),
    Conclusion = ifelse(Non_Inferior, 
                       "**Non-inferior to threshold**", 
                       "Not established as non-inferior")
  ) %>%
  select(Hypothesis, Success_Rate, Lower_Bound, Conclusion) %>%
  knitr::kable(caption = "Summary of Non-inferiority Tests (threshold = 0.35)")
```

## Bayesian Analysis for H1 and H3

```{r warning=FALSE}
# Add this at the beginning of your Bayesian analysis chunk
# Suppress compilation messages
suppressMessages({
  suppressWarnings({
    invisible(capture.output({
      library(brms)
    }))
  })
})

# Function to run Bayesian analysis with extra suppression
run_bayesian_test <- function(data_filtered, hypothesis_name, condition_desc) {
  # Using weakly informative priors
  prior <- c(set_prior("normal(0, 1.5)", class = "Intercept"))
  
  # Capture and suppress all output during model fitting
  invisible(capture.output({
    suppressMessages({
      suppressWarnings({
        # Fit Bayesian model
        model <- brm(
          success ~ 1,
          data = data_filtered,
          family = bernoulli(),
          prior = prior,
          chains = 4,
          iter = 2000,
          warmup = 1000,
          seed = 123,
          silent = 2,
          refresh = 0
        )
      })
    })
  }))
  
  # Extract posterior samples
  posterior <- posterior_samples(model)
  intercept_samples <- posterior$b_Intercept
  prob_samples <- plogis(intercept_samples)
  
  # Calculate 95% CI
  ci <- quantile(prob_samples, probs = c(0.025, 0.975))
  
  # Calculate probability that true success rate > 0.5
  prob_above_chance <- mean(prob_samples > 0.5)
  prob_below_chance <- mean(prob_samples < 0.5)
  
  # Print results
  cat("------------------------------------------------------\n")
  cat(paste0(hypothesis_name, " (Bayesian analysis): ", condition_desc, "\n"))
  cat("------------------------------------------------------\n")
  cat("Estimated success probability:", round(mean(prob_samples), 3), "\n")
  cat("95% credible interval:", round(ci[1], 3), "to", round(ci[2], 3), "\n")
  cat("Probability that true success rate > 0.5:", round(prob_above_chance, 3), "\n")
  cat("Probability that true success rate < 0.5:", round(prob_below_chance, 3), "\n\n")
  
  # Test if CI includes 0.5
  includes_chance <- ci[1] <= 0.5 && ci[2] >= 0.5
  
  if (includes_chance) {
    cat("Result: The 95% credible interval includes 0.5, suggesting the model's performance is not significantly different from chance.\n\n")
  } else if (ci[1] > 0.5) {
    cat("**Result: The 95% credible interval is entirely above 0.5, suggesting the model performs significantly worse than chance.**\n\n")
  } else {
    cat("**Result: The 95% credible interval is entirely below 0.5, suggesting the model performs significantly better than chance.**\n\n")
  }
  
  return(list(
    mean_prob = mean(prob_samples),
    ci = ci,
    prob_above_chance = prob_above_chance,
    prob_below_chance = prob_below_chance,
    includes_chance = includes_chance
  ))
}

# Run Bayesian analyses for key hypotheses
# H1a: ELIZA (manipulation check)
h1a_bayes <- run_bayesian_test(
  games %>% filter(ai_model == "eliza_prolific"),
  "H1a", 
  "Bayesian test for ELIZA detectability"
)

# H1b: Llama with persona
h1b_bayes <- run_bayesian_test(
  games.persona.first %>% filter(ai_model == "llama-405b_quinn_prolific"),
  "H1b", 
  "Bayesian test for Llama with persona detectability"
)

# H1c: GPT-4.5 with persona
h1c_bayes <- run_bayesian_test(
  games.persona.first %>% filter(ai_model == "gpt-4.5_quinn_prolific"),
  "H1c", 
  "Bayesian test for GPT-4.5 with persona detectability"
)

# H3a: GPT-4.5 with minimal prompt
h3a_bayes <- run_bayesian_test(
  games %>% filter(ai_model == "gpt-4.5_minimal_prolific"),
  "H3a", 
  "Bayesian test for GPT-4.5 with minimal prompt detectability"
)

# H3b: Llama with minimal prompt
h3b_bayes <- run_bayesian_test(
  games %>% filter(ai_model == "llama-405b_minimal_prolific"),
  "H3b", 
  "Bayesian test for Llama with minimal prompt detectability"
)

# Summarize Bayesian analyses
bayes_summary <- data.frame(
  Hypothesis = c("H1a: ELIZA", "H1b: Llama (persona)", "H1c: GPT-4.5 (persona)",
                "H3a: GPT-4.5 (no-persona)", "H3b: Llama (no-persona)"),
  Success_Rate = c(h1a_bayes$mean_prob, h1b_bayes$mean_prob, h1c_bayes$mean_prob,
                  h3a_bayes$mean_prob, h3b_bayes$mean_prob),
  CI_Lower = c(h1a_bayes$ci[1], h1b_bayes$ci[1], h1c_bayes$ci[1],
              h3a_bayes$ci[1], h3b_bayes$ci[1]),
  CI_Upper = c(h1a_bayes$ci[2], h1b_bayes$ci[2], h1c_bayes$ci[2],
              h3a_bayes$ci[2], h3b_bayes$ci[2]),
  Includes_Chance = c(h1a_bayes$includes_chance, h1b_bayes$includes_chance, 
                     h1c_bayes$includes_chance, h3a_bayes$includes_chance,
                     h3b_bayes$includes_chance)
)

# Print summary table
bayes_summary %>%
  mutate(
    Success_Rate = round(Success_Rate, 3),
    CI_Lower = round(CI_Lower, 3),
    CI_Upper = round(CI_Upper, 3),
    Conclusion = ifelse(Includes_Chance, 
                       "Not different from chance", 
                       ifelse(CI_Lower > 0.5,
                             "**Worse than chance**",
                             "**Better than chance**"))
  ) %>%
  select(Hypothesis, Success_Rate, CI_Lower, CI_Upper, Conclusion) %>%
  rename(`95% CI Lower` = CI_Lower, `95% CI Upper` = CI_Upper) %>%
  knitr::kable(caption = "Summary of Bayesian Analyses")
```

# Demographics

## Familiarity with GPT

```{r}
# Effect of LLM knowledge on detection accuracy
if ("familiarity_with_GPT" %in% names(games)) {
  llm_knowledge_model <- glm(
    success ~ familiarity_with_GPT, 
    family = "binomial",
    data = games
  )
  
  cat("Effect of LLM knowledge on detection accuracy\n")
  cat("------------------------------------------------------\n")
  print(summary(llm_knowledge_model))
  
  # Visualize
  games %>%
    group_by(familiarity_with_GPT) %>%
    summarize(
      accuracy = mean(success),
      se = sqrt(accuracy * (1 - accuracy) / n()),
      n = n(),
      .groups = "drop"
    ) %>%
    ggplot(aes(x = factor(familiarity_with_GPT), y = accuracy)) +
    geom_bar(stat = "identity", fill = "lightblue") +
    geom_errorbar(
      aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
      width = 0.2
    ) +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
    labs(
      x = "LLM Knowledge Level",
      y = "Detection Accuracy",
      title = "Effect of LLM Knowledge on Detection Accuracy"
    ) +
    theme_minimal() +
    scale_x_discrete(labels = c("None", "Some", "High", "Research")) +
    scale_y_continuous(limits = c(0, 1))
}
```

## Chatbot Interaction Frequency


```{r}
# Effect of Chatbot Interaction frequency on detection accuracy

chatbot_interaction_frequency_model <- glm(
  success ~ familiarity_with_GPT, 
  family = "binomial",
  data = games
)

cat("Effect of Chatbot interaction frequency on detection accuracy\n")
cat("-------------------------------------------------------------\n")
print(summary(chatbot_interaction_frequency_model))

# Visualize
games %>%
  group_by(chatbot_interaction_frequency) %>%
  filter(chatbot_interaction_frequency > 0) %>%
  summarize(
    accuracy = mean(success),
    se = sqrt(accuracy * (1 - accuracy) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = factor(chatbot_interaction_frequency), y = accuracy)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbar(
    aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
    width = 0.2
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Chatbot Interaction Frequency",
    y = "Detection Accuracy",
    title = "Effect of CIF on Detection Accuracy"
  ) +
  theme_minimal() +
  scale_x_discrete(labels = c("None", "Some", "High", "Research")) +
  scale_y_continuous(limits = c(0, 1))
```

## Gender

```{r}

# Effect of gender on detection accuracy
if ("gender" %in% names(games)) {
  gender_model <- glm(
    success ~ gender, 
    family = "binomial",
    data = games %>% filter(gender %in% c("M", "F", "N"))
  )
  
  cat("\nEffect of gender on detection accuracy\n")
  cat("------------------------------------------------------\n")
  print(summary(gender_model))
  
  # Visualize
  games %>%
    filter(gender %in% c("M", "F", "N")) %>%
    group_by(gender) %>%
    summarize(
      accuracy = mean(success),
      se = sqrt(accuracy * (1 - accuracy) / n()),
      n = n(),
      .groups = "drop"
    ) %>%
    ggplot(aes(x = factor(gender), y = accuracy)) +
    geom_bar(stat = "identity", fill = "lightblue") +
    geom_errorbar(
      aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
      width = 0.2
    ) +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
    labs(
      x = "Gender",
      y = "Detection Accuracy",
      title = "Effect of Gender on Detection Accuracy"
    ) +
    theme_minimal() +
    scale_x_discrete(labels = c("F", "M", "N.B.")) +
    scale_y_continuous(limits = c(0, 1))
}
```


## Education

```{r}

# Effect of education on detection accuracy
education_model <- glm(
  success ~ education, 
  family = "binomial",
  data = games %>% filter(education > 0)
)

cat("\nEffect of Education on detection accuracy\n")
cat("------------------------------------------------------\n")
print(summary(education_model))

# Visualize
games %>%
  filter(education > 0) %>%
  group_by(education) %>%
  summarize(
    accuracy = mean(success),
    se = sqrt(accuracy * (1 - accuracy) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = factor(education), y = accuracy)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbar(
    aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
    width = 0.2
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Education",
    y = "Detection Accuracy",
    title = "Effect of Education on Detection Accuracy"
  ) +
  theme_minimal() +
  scale_x_discrete(labels = c("HS", "UG", "PG")) +
  scale_y_continuous(limits = c(0, 1))
```

## Age

```{r}

# Effect of age on detection accuracy
if ("age" %in% names(games)) {
  age_model <- glm(
    success ~ age, 
    family = "binomial",
    data = games %>% filter(age > 0, age < 100)
  )
  
  cat("\nEffect of age on detection accuracy\n")
  cat("------------------------------------------------------\n")
  print(summary(age_model))
  
  # Visualize
  games %>%
    filter(age > 0, age < 100) %>%
    ggplot(aes(x = age, y = as.numeric(success))) +
    geom_smooth(method = "glm", formula = "y ~ x", 
                method.args = list(family = "binomial"),
                color = "blue", fill = "lightblue") +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
    labs(
      x = "Age",
      y = "Detection Accuracy",
      title = "Effect of Age on Detection Accuracy"
    ) +
    theme_minimal() +
    scale_y_continuous(limits = c(0, 1))
}

```

## Trial index

```{r}

# Effect of trial number on detection accuracy
trial_model <- glm(
  success ~ interrogator_game_index, 
  family = "binomial",
  data = games
)

cat("\nEffect of trial number on detection accuracy\n")
cat("------------------------------------------------------\n")
print(summary(trial_model))

# Visualize
games %>%
  group_by(interrogator_game_index) %>%
  filter(interrogator_game_index <= 8) %>%  # Limit to reasonable number of trials
  summarize(
    accuracy = mean(success),
    se = sqrt(accuracy * (1 - accuracy) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = interrogator_game_index, y = accuracy)) +
  geom_point(size = 3) +
  geom_line() +
  geom_errorbar(
    aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
    width = 0.2
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Trial Number",
    y = "Detection Accuracy",
    title = "Effect of Trial Number on Detection Accuracy"
  ) +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1, 8, by = 1)) +
  scale_y_continuous(limits = c(0, 1))
```

## AI Intelligence


```{r}
# Effect of AI Intelligence frequency on detection accuracy

intelligence_model <- glm(
  success ~ intelligence, 
  family = "binomial",
  data = games %>% filter(intelligence > 0)
)

cat("Effect of AI intelligence on detection accuracy\n")
cat("-------------------------------------------------------------\n")
print(summary(intelligence_model))

# Visualize
games %>%
  group_by(intelligence) %>%
  filter(intelligence > 0) %>%
  summarize(
    accuracy = mean(success),
    se = sqrt(accuracy * (1 - accuracy) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = factor(intelligence), y = accuracy)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbar(
    aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
    width = 0.2
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "AI Intelligence",
    y = "Detection Accuracy",
    title = "Effect of AI Intelligence on Detection Accuracy"
  ) +
  theme_minimal() +
  # scale_x_discrete(labels = c("Low", "Medium", "High")) +
  scale_y_continuous(limits = c(0, 1))



```

## AI Emotion

```{r}

# Effect of AI Emotion frequency on detection accuracy

emotion_model <- glm(
  success ~ emotion, 
  family = "binomial",
  data = games %>% filter(emotion > 0)
)

cat("Effect of AI emotion on detection accuracy\n")
cat("-------------------------------------------------------------\n")
print(summary(emotion_model))

# Visualize
games %>%
  group_by(emotion) %>%
  filter(emotion > 0) %>%
  summarize(
    accuracy = mean(success),
    se = sqrt(accuracy * (1 - accuracy) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = factor(emotion), y = accuracy)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  geom_errorbar(
    aes(ymin = accuracy - 1.96 * se, ymax = accuracy + 1.96 * se),
    width = 0.2
  ) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "AI Emotion",
    y = "Detection Accuracy",
    title = "Effect of AI Emotion on Detection Accuracy"
  ) +
  theme_minimal() +
  # scale_x_discrete(labels = c("Low", "Medium", "High")) +
  scale_y_continuous(limits = c(0, 1))
```


## Accuracy Estimate

```{r}

# Effect of accuracy estimate frequency on detection accuracy

accuracy_estimate_model <- glm(
  success ~ accuracy_estimate, 
  family = "binomial",
  data = games %>%
    group_by(
      interrogator_user_id
    ) %>%
    mutate(
      n_games = n(),
      accuracy_estimate = pmin(n_games, accuracy_estimate),
      accuracy_estimate = accuracy_estimate / n_games
    )
)

cat("Effect of accuracy estimate on detection accuracy\n")
cat("-------------------------------------------------------------\n")
print(summary(accuracy_estimate_model))

# Visualize
games %>%
  group_by(
      interrogator_user_id
    ) %>%
    mutate(
      n_games = n(),
      accuracy_estimate = pmin(n_games, accuracy_estimate),
      accuracy_estimate = accuracy_estimate / n_games,
      .groups="drop"
    ) %>%
  group_by(accuracy_estimate) %>%
  # filter(accuracy_estimate > 0) %>%
  summarize(
    accuracy = mean(success),
    se = sqrt(accuracy * (1 - accuracy) / n()),
    n = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = accuracy_estimate, y = accuracy)) +
  geom_smooth(method = "lm", formula = "y ~ x",
              color = "blue", fill = "lightblue") +
  stat_summary_bin(fun = mean, geom = "point", size = 2) +
  stat_summary_bin(fun.data = mean_se, geom = "errorbar", width = 0.2) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  labs(
    x = "Accuracy Estimate",
    y = "Detection Accuracy",
    title = "Effect of Accuracy Estimate on Detection Accuracy"
  ) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 1))

```

```


